---
title: "stressor_map_binned"
author: "Juliette"
date: "4/20/2020"
editor_options: 
  chunk_output_type: console
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

options(scipen = 999)
```


```{r}
library(tidyverse)
library(dplyr)
library(raster)
library(tidyverse)
library(sf)
library("rnaturalearth")
library(rgdal)
library(here)

gall_peters <- "+proj=cea +lon_0=0 +x_0=0 +y_0=0 +lat_ts=45 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"
```


Reclassify to 4 categories 
Chicken
```{r}
chicken <- raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/chickens_cumulative_stress.tif")

chicken_disturb<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/chickens_disturbance_per_cell.tif")

chicken_df<-rasterToPoints(chicken) %>% 
  as.data.frame()

chicken_disturb_df<-rasterToPoints(chicken_disturb) %>% 
  as.data.frame()

disturb_quant<-full_join(chicken_df, chicken_disturb_df)

chicken_df_no0<-chicken_df %>% 
  filter(!chickens_cumulative_stress<=0)

##remove NAs just for quantiles
chicken_quant <- chicken
values(chicken_quant)[values(chicken_quant) <=0 ] = NA

quant_0 <- quantile(chicken_quant, 0) 
quant_45 <- quantile(chicken_quant, 0.45)
quant_90 <- quantile(chicken_quant, 0.90)

length(which(chicken_df$chickens_cumulative_stress==0))/nrow(chicken_df)
length(which(chicken_df$chickens_cumulative_stress<quant_45))/nrow(chicken_df)

sub_disturb_quant<- disturb_quant %>% 
  filter(chickens_cumulative_stress<quant_45)

test<- disturb_quant %>% 
  filter(chickens_cumulative_stress>quant_45)


max <- maxValue(chicken_quant)
## reclassify to 4 bins
matrix <-c(0, 0, 0,
           0, quant_45, 1,
           quant_45, quant_90, 2, 
           quant_90, max, 3)


matrix_chicken <- matrix(matrix, ncol=3, byrow=TRUE)

recl_chicken <- reclassify(chicken, matrix_chicken)
plot(recl_chicken)
```

# Cell count

```{r}
recl_chicken_df<-rasterToPoints(recl_chicken) %>% 
  as.data.frame()

length(which(recl_chicken_df$chickens_cumulative_stress == 3))
```

Salmon
```{r}
salmon <- raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/salmon_cumulative_stress.tif")

salmon_df<-rasterToPoints(salmon) %>% 
  as.data.frame()

salmon_df_no0<-salmon_df %>% 
  filter(!salmon_cumulative_stress<=0)


##remove NAs just for quantiles
salmon_quant <- salmon
values(salmon_quant)[values(salmon_quant) <=0 ] = NA

quant_0 <- quantile(salmon_quant, 0)  
quant_45 <- quantile(salmon_quant, 0.45)  
quant_90 <- quantile(salmon_quant, 0.90) 
max <- maxValue(salmon_quant)

## reclassify to 4 bins
matrix <-c(0, 0, 0,
           0, quant_45 , 1,
           quant_45 , quant_90 , 2, 
           quant_90 , max, 3)


matrix_salmon <- matrix(matrix, ncol=3, byrow=TRUE)

recl_salmon <- reclassify(salmon, matrix_salmon)

## what do these look like binned
plot(recl_salmon)
plot(recl_chicken)
unique(recl_salmon)

```

```{r}
recl_salmon_df<-rasterToPoints(recl_salmon) %>% 
  as.data.frame()

length(which(recl_salmon_df$salmon_cumulative_stress == 3))
```
Combine the two to end up with 16 different categories

```{r}
salmon_df <- as.data.frame(recl_salmon, xy= TRUE)
chicken_df <- as.data.frame(recl_chicken, xy = TRUE)

combo <- left_join(salmon_df, chicken_df)

combo_assign <- combo %>% 
  rename(salmon = salmon_cumulative_stress) %>% 
  rename(chicken = chickens_cumulative_stress) %>% 
  rowwise() %>% 
  mutate(color_assign = ifelse(salmon == 0 & chicken == 0, 13,
                        ifelse(salmon == 0 & chicken == 1, 9,
                        ifelse(salmon == 0 & chicken == 2, 5,
                        ifelse(salmon == 0 & chicken == 3, 1,

                        ifelse(salmon == 1 & chicken == 0, 14, 
                        ifelse(salmon == 1 & chicken == 1, 10,
                        ifelse(salmon == 1 & chicken == 2, 6,
                        ifelse(salmon == 1 & chicken == 3, 2,

                        ifelse(salmon == 2 & chicken == 0, 15,
                        ifelse(salmon == 2 & chicken == 1, 11,
                        ifelse(salmon == 2 & chicken == 2, 7,
                        ifelse(salmon == 2 & chicken == 3, 3,

                        ifelse(salmon == 3 & chicken == 0, 16,
                        ifelse(salmon == 3 & chicken == 1, 12,
                        ifelse(salmon == 3 & chicken == 2, 8, 
                        ifelse(salmon == 3 & chicken == 3, 4,

                             NA)))))))))))))))))

rast_combo_assign <- combo_assign %>% 
  dplyr::select(x,y,color_assign) %>% 
  rasterFromXYZ(crs = gall_peters)

##look at them as a gut check that it works
plot(recl_chicken)
plot(recl_salmon)
plot(rast_combo_assign)
#length(unique(combo_assign$color_assign))
#unique(combo_assign$color_assign))

```

# Figure of any overlap: Figure 1C

We don't want 

```{r}
non_overlap<-c(13, 9, 5, 1, 14, 15, 16)

anyoverlap<-rast_combo_assign
anyoverlap[anyoverlap %in% non_overlap]<-NA
anyoverlap[anyoverlap>1]<-1

anyoverlap_spdf <- as(anyoverlap, "SpatialPixelsDataFrame")
anyoverlap_df <- as.data.frame(anyoverlap_spdf)
colnames(anyoverlap_df) <- c("value", "x", "y")

land <- ne_countries(scale = "medium", returnclass = "sf") 
land <- land[!land$sov_a3 == "ATA",]
land <- st_transform(land, crs=gall_peters)

```

```{r}
ggplot() +
  geom_raster(data = anyoverlap_df, aes(x = x, y = y, fill = value)) +
  geom_sf(data = land, fill = "transparent", col = "black", lwd = 0.5) +
  labs(fill = "") +
  theme_minimal()
```

```{r}
ggsave(here("_analysis/figures/maps/Any_overlap_map.png"), dpi=300, width=5, height=3)
```

```{r}
png(here(sprintf("_analysis/figures/maps/Any_overlap_map.png", system)), res=500, width=5, height=3, units="in")

plot(anyoverlap, col = "coral1")

dev.off()
```

```{r}
col_cont <- c("#E42879", "#DA4C93", "#9F406E", "#561276", 
         "#F097C9", "#BB6B95", "#8e29bd", "#5e9e90", 
         "#F6CEE2", "#BF87DA", "#95BFC0", "#4dc4ac",
         "#F9F9F91A", "#D0EBE5", "#89D8C8", "#048481")

col_cont2<-c("#f00f8b", "#ee87e8",  "#92a4ff", "#0d89ff",
  "#fa7b86", "#fde3fc",  "#d1faff", "#2bc1ff",
  "#f8934c", "#fff3c1", "#b9fff0",  "#31c7d4",
  "#F9F9F91A", "#a3b53a", "#46c36e", "#27996d")


col_discrete <- c("1" = "#E42879",
                     "2" = "#DA4C93",
                     "3" = "#9F406E",
                     "4" = "#561276",
                     "5" = "#F097C9",
                     "6" =  "#BB6B95",
                     "7" = "#8e29bd",
                     "8" = "#5e9e90",
                     "9" = "#F6CEE2",
                     "10" = "#BF87DA",
                     "11" = "#95BFC0",
                     "12" = "#4dc4ac", 
                     "13" = "#F9F9F91A", #white
                     "14" = "#D0EBE5", 
                     "15" = "#89D8C8",
                     "16" = "#048481")  



col_discrete2<-c("16" = "#27996d",
                     "15" = "#46c36e",
                     "14" = "#a3b53a",
                     "13" = "#F9F9F91A", #white
                     "12" = "#31c7d4",
                     "11" = "#b9fff0",
                     "10" = "#fff3c1",
                     "9" = "#f8934c",
                     "8" = "#2bc1ff",
                     "7" = "#d1faff",
                     "6" = "#fde3fc",
                     "5" = "#fa7b86", 
                     "4" = "#0d89ff", 
                     "3" = "#92a4ff", 
                     "2" = "#ee87e8",
                     "1" = "#f00f8b") 



# Plot only salmon pressures
#14,15,16
#col_cont <- c("#F9F9F91A", "#F9F9F91A", "#F9F9F91A", "#F9F9F91A", 
#         "#F9F9F91A", "#F9F9F91A", "#F9F9F91A", "#F9F9F91A", 
#         "#F9F9F91A", "#F9F9F91A", "#F9F9F91A", "#F9F9F91A",
#         "#F9F9F91A", "#D0EBE5", "#89D8C8", "#048481")

# Plot only chicken pressures
# 9,5,1
#col_cont <- c("#E42879", "#F9F9F91A", "#F9F9F91A", "#F9F9F91A", 
#         "#F097C9", "#F9F9F91A", "#F9F9F91A", "#F9F9F91A", 
#         "#F6CEE2", "#F9F9F91A", "#F9F9F91A", "#F9F9F91A",
#         "#F9F9F91A","#F9F9F91A","#F9F9F91A", "#F9F9F91A")
```


Map the raster with the color palette
```{r}
cuts <- c(0:16) #set breaks
  
par(mar=c(1,1,1,1))
plot<-raster::plot(rast_combo_assign, breaks=cuts, col=col_cont2, add = T)

```


Making legend
```{r}
legend <- read_csv(here("_analysis/figures/overlap_map/data/legend_values.csv")) %>% 
  mutate(value = as.character(value))

legend_graph <- ggplot(data = legend, aes(x = salmon, y = chicken)) +
  geom_tile(aes(fill = value)) +
  theme_minimal() +
  scale_fill_manual("value", values=col_discrete2)+
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "none",
        panel.grid.minor = element_blank(),
        text = element_text(size=15))
legend_graph

ggsave(here("_analysis/overlap_map/outputs/overlap_legend_newcolors.jpg"), width=5, height=3, dpi=300)
  
```

Overlay and save the raster with land outlines
```{r}

land <- ne_countries(scale = "medium", returnclass = "sp") 
land <- land[!land$sov_a3 == "ATA",]
land <- st_as_sf(land)
land <- st_transform(land, crs=gall_peters)
land <- as(land, "Spatial")
plot(land)

grDevices::png(here("_analysis/figures/overlap_map/outputs/overlap_map_newcolors.png"), res=500, width=6, height=3, units = "in")
par(oma=c(1,1,1,0)) # bottom, left, top, and right
par(mfrow=c(1, 1), mar=c(1, 0, 1, 0), new=TRUE)

plot(rast_combo_assign, 
     breaks=cuts, 
     col=col_cont2,
     axes=FALSE,
     box=FALSE,
    # add=TRUE,
     legend=FALSE,
     axis.args = list(cex.axis = 0.6, cex.sub=0.6, cex=0.6, lwd.ticks=1))

plot(land, border="#2F4F4F" , lwd=0.3, add=TRUE)

grDevices::dev.off()

```

Create the bar graph for the total number of cells 

maybe factor order levels with the 3 chicken categories on the left only chicken no salmon, and then the three only salmon categories ont he right and then the mix in the middle

```{r}
cell_count <- combo_assign %>% 
  count(color_assign) %>% 
  rename(number_cells = n) %>% 
  filter(color_assign != is.na(color_assign)) %>% 
  mutate(category = case_when(color_assign == 1 ~ "high chicken\nzero salmon",
                              color_assign == 2 ~ "high chicken\nlow salmon",
                              color_assign == 3 ~ "high chicken\nmedium salmon",
                              color_assign == 4 ~ "high chicken\nhigh salmon",
                              color_assign == 5 ~ "medium chicken\nzero salmon",
                              color_assign == 6 ~ "medium chicken\nlow salmon",
                              color_assign == 7 ~ "medium chicken\nmedium salmon",
                              color_assign == 8 ~ "medium chicken\nhigh salmon",
                              color_assign == 9 ~ "low chicken\nzero salmon",
                              color_assign == 10 ~ "low chicken\nlow salmon",
                              color_assign == 11 ~ "low chicken\nmedium salmon",
                              color_assign == 12 ~ "low chicken\nhigh salmon",
                              color_assign == 13 ~ "zero chicken\nzero salmon",
                              color_assign == 14 ~ "zero chicken\nlow salmon",
                              color_assign == 15 ~ "zero chicken\nmedium salmon",
                              color_assign == 16 ~ "zero chicken\nhigh salmon")) %>% 
  mutate(category = as.factor(category)) %>% 
  #filter(color_assign != 13) %>% 
  mutate(color_assign = as.character(color_assign))

cell_count<-cell_count %>% 
  mutate(prop_cells = number_cells/sum(cell_count$number_cells))


bar_graph <- ggplot(cell_count, aes(x = category, y = number_cells/1000000, fill= color_assign))+
  geom_bar(stat = "identity", colour="black") +
  theme_minimal()+
  ylab("Number of cells (millions)")+
  xlab("")+
  ylim(c(0,5))+
  theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        legend.position = "none",
        text = element_text(size=8),
        axis.text.x = element_text(angle = 90, hjust=0))+
  scale_fill_manual("color_assign", values=col_discrete2)
 
bar_graph

ggsave(here("_analysis/figures/overlap_map/outputs/bar_graph_with_zero.jpg"),height = 5, width = 6,  dpi=300) 
#ggsave("_analysis/int_figs/bar_graph_no_zero.jpg", height = 2, width = 12, dpi=300) 
 
write.csv(cell_count, here("_analysis/figures/overlap_map/data/cell_count.csv"))
```

```{r}
# Any overlap of chicken and salmon

prop_overlap<- cell_count %>% 
  filter(!category %in% as.factor(c("high chicken\nzero salmon", "medium chicken\nzero salmon", "low chicken\nzero salmon", "zero chicken\nzero salmon", "zero chicken\nmedium salmon", "zero chicken\nhigh salmon")))
```


Create a circle grid plot with the circles the size of the proportion of cells 
**make sure you know what the cell count is including. zero/zero or not
```{r}
circle_legend <- legend %>% 
  rename(color_assign = value) %>% 
  left_join(cell_count) %>% 
  mutate(color_assign = as.factor(color_assign))

circle_legend_plot <- ggplot(circle_legend, aes(x= salmon, y=chicken)) +
  geom_point(aes(size = prop_cells, color=color_assign)) +
    geom_point(aes(size = prop_cells, color=color_assign), shape=21, color="gray") +
  theme_minimal() +
   theme(panel.border = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = "none",
        axis.text.x = element_text(angle=360, size=12),
          axis.text.y = element_text(angle=90, size=12, vjust=-2, hjust=0.4),
        axis.title.x = element_text(size = 13),
        axis.title.y = element_text(size = 13)) +
  scale_size_continuous(range = c(5, 36)) +
  scale_color_manual("color_assign", values=col_discrete2) +
  scale_x_continuous(breaks=c(0,1,2,3), labels=c("Zero", "0 to 45th",
                              "45 to 90th", ">90th"), limits=c(-0.5, 3.5), name="Salmon quantile") +
  scale_y_continuous(breaks=c(0,1,2,3), labels=c("Zero", "0 to 45th",
                              "45 to 90th", ">90th"), limits=c(-0.5, 3.5), name="Chicken quantile")

circle_legend_plot


```


```{r}
ggsave(here("_analysis/figures/overlap_map/outputs/overlap_circle_legend_newcolors.jpg"), width=6, height=4, dpi=300,  bg = "white") 
```







