---
title: "Untitled"
author: "Caitie"
date: "08/09/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(raster)
library(tidyverse)
library(ggplot2)
library(here)
library(ggrepel)
library(png)
library(grid)
library(RCurl)
library(patchwork)
library(countrycode)
```

# Consumption data by country

Data from: http://www.fao.org/faostat/en/#data/FBS

Food is in 1000 tonnes
Data refer to the total amount of the commodity available as human food during the reference period. Data include the commodity in question, as well as any commodity derived therefrom as a result of further processing. Food from maize, for example, comprises the amount of maize, maize meal and any other products derived therefrom available for human consumption. Food from milk relates to the amounts of milk as such, as well as the fresh milk equivalent of dairy products. Source: FAO. 1986. The ICS users' manual. Interlinked computer strorage and processing system of food and agricultural commodity data. Rome.


Food supply is in kg
Production + imports - exports + changes in stocks (decrease or increase) = food supply for domestic utilization.There are various ways of defining supply and, in fact, various concepts are in use. The elements involved are production, imports, exports and changes in stocks (increase or decrease). There is no doubt that production, imports and stock changes (either decrease or increase in stocks) are genuine supply elements. Source: FAO Statistics Division

```{r}
consump<-read.csv(here("consumption_data/consumption_2016.csv")) %>% 
  mutate(iso3c = countrycode(Area, "country.name", "iso3c"))
```

Chicken

```{r}
chick_consump<-consump %>% 
  filter(Item == "Poultry Meat",
         !Area == "China, mainland") %>% 
  dplyr::select(iso3c, Value, Element) %>% 
  pivot_wider(., names_from = Element, values_from = Value) %>% 
  rename(food = Food,
         food_supply = 'Food supply quantity (kg/capita/yr)') %>% 
  mutate(food = food * 1000)

```


Marine fish

```{r}

salmon_consump<-consump %>% 
  filter(Item ==  "Marine Fish, Other",
         !Area == "China, mainland") %>% 
  dplyr::select(iso3c, Value, Element) %>% 
  pivot_wider(., names_from = Element, values_from = Value) %>% 
  rename(food = Food,
         food_supply = 'Food supply quantity (kg/capita/yr)') %>% 
  mutate(food = food * 1000)

```

# CHI data by country

```{r}
country_average<-read.csv(here("_analysis/data/zonal_extract/average_rescaled_pressures_country.csv"))
country_average_nozeros<-read.csv(here("_analysis/data/zonal_extract/average_rescaled_pressures_country_nozeros.csv"))
country_sum<-read.csv(here("_analysis/data/zonal_extract/sum_rescaled_pressures_country.csv"))
```

Chicken

```{r}
country_chicken<- country_average %>% 
  filter(animal_system == "broiler") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total))

country_chicken

country_chicken_nozeros<- country_average_nozeros %>% 
  filter(animal_system == "broiler") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total))

country_chicken_nozeros

country_chicken_sum<- country_sum %>% 
  filter(animal_system == "broiler") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total))

country_chicken_sum
```


```{r}
country_chicken_feed<- country_average %>% 
  filter(animal_system == "broiler", source == "feed") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(feed = total)

country_chicken_feed

country_chicken_feed_nozeros<- country_average_nozeros %>% 
  filter(animal_system == "broiler", source == "feed") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(feed = total)

country_chicken_feed_nozeros

country_chicken_feed_sum<- country_sum %>% 
  filter(animal_system == "broiler", source == "feed") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(feed = total)

country_chicken_feed_sum
```

```{r}
country_chicken_farm<- country_average %>% 
  filter(animal_system == "broiler", source == "farm") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(farm = total)

country_chicken_farm

country_chicken_farm_nozeros<- country_average_nozeros %>% 
  filter(animal_system == "broiler", source == "farm") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(farm = total)

country_chicken_farm_nozeros

country_chicken_farm_sum<- country_sum %>% 
  filter(animal_system == "broiler", source == "farm") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(farm = total)


country_chicken_farm_sum
```

Salmon

```{r}
country_salmon<- country_average %>% 
  filter(animal_system == "salmon") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total))

country_salmon

country_salmon_nozeros<- country_average_nozeros %>% 
  filter(animal_system == "salmon") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total))

country_salmon_nozeros

country_salmon_sum<- country_sum %>% 
  filter(animal_system == "salmon") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total))

country_salmon_sum
```

```{r}
country_salmon_feed<- country_average %>% 
  filter(animal_system == "salmon", source == "feed") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(feed = total)

country_salmon_feed

country_salmon_feed_nozeros<- country_average_nozeros %>% 
  filter(animal_system == "salmon", source == "feed") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(feed = total)

country_salmon_feed_nozeros

country_salmon_feed_sum<- country_sum %>% 
  filter(animal_system == "salmon", source == "feed") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(feed = total)


country_salmon_feed_sum
```

```{r}
country_salmon_farm<- country_average %>% 
  filter(animal_system == "salmon", source == "farm") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(farm = total)

country_salmon_farm

country_salmon_farm_nozeros<- country_average_nozeros %>% 
  filter(animal_system == "salmon", source == "farm") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(farm = total)

country_salmon_farm_nozeros


country_salmon_farm_sum<- country_sum %>% 
  filter(animal_system == "salmon", source == "farm") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total)) %>% 
  rename(farm = total)

country_salmon_farm_sum
```

# Join data

Chicken

```{r}
chick_dat<-full_join(country_chicken, chick_consump, by = "iso3c") %>% 
  full_join(., country_chicken_feed, by = "iso3c") %>% 
  full_join(., country_chicken_farm, by = "iso3c")

chick_dat_nozeros<-full_join(country_chicken_nozeros, chick_consump, by = "iso3c") %>% 
  full_join(., country_chicken_feed_nozeros, by = "iso3c") %>% 
  full_join(., country_chicken_farm_nozeros, by = "iso3c")

chick_dat_sum<-full_join(country_chicken_sum, chick_consump, by = "iso3c") %>% 
  full_join(., country_chicken_feed_sum, by = "iso3c") %>% 
  full_join(., country_chicken_farm_sum, by = "iso3c")
```


Salmon
```{r}
salmon_dat<-full_join(country_salmon, salmon_consump, by = "iso3c") %>% 
  full_join(., country_salmon_feed, by = "iso3c") %>% 
  full_join(., country_salmon_farm,by = "iso3c") 

salmon_dat_nozeros<-full_join(country_salmon_nozeros, salmon_consump, by = "iso3c") %>% 
  full_join(., country_salmon_feed_nozeros, by = "iso3c") %>% 
  full_join(., country_salmon_farm_nozeros,by = "iso3c") 

salmon_dat_sum<-full_join(country_salmon_sum, salmon_consump, by = "iso3c") %>% 
  full_join(., country_salmon_feed_sum, by = "iso3c") %>% 
  full_join(., country_salmon_farm_sum,by = "iso3c") 
```

# Plotting function

```{r}
consump_plot<-function(data, x, y){
  ggplot(data, aes(y = y, x= x, label = labels))+
  geom_point() +
  geom_smooth(formula = y~x, method = "lm") +
  #annotation_custom(, ymin = 2.5, ymax = 3, xmin = 15, xmax=18) +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(),
panel.background = element_blank(), axis.line = element_line(colour = "black"),
legend.position = "none") +
  #xlab(xlabel) +
  #ylab(ylabel) +
  geom_text_repel()
  
}
```


# Chicken plots of food vs. CHI

Chicken

```{r}
chick_dat<-chick_dat %>% 
  mutate(labels = ifelse(total>0.5|food>3000000, iso3c, NA))

consump_plot(chick_dat, chick_dat$food/1000000, chick_dat$total)
```

```{r}
cor.test(chick_dat$total, chick_dat$food, method = "pearson")
```
```{r}
chick_dat_nozeros<-chick_dat_nozeros %>% 
  mutate(labels = ifelse(total>0.5|food>3000000, iso3c, NA))

consump_plot(chick_dat_nozeros, chick_dat_nozeros$food/1000000, chick_dat_nozeros$total)
```

```{r}
chick_dat_sum<-chick_dat_sum %>% 
  mutate(labels = ifelse(total>5000|food>2000000, iso3c, NA))

consump_plot(chick_dat_sum, chick_dat_sum$food/1000000, chick_dat_sum$total/10000)
```

```{r}
cor.test(chick_dat_sum$total, chick_dat_sum$food, type = "pearson")
```
# Chicken feed pressures vs food

```{r}
chick_dat<-chick_dat %>% 
  mutate(labels = ifelse(feed>0.1|food>3000000, iso3c, NA))

consump_plot(chick_dat, chick_dat$food/1000000, chick_dat$feed)

```
```{r}
chick_dat_nozeros<-chick_dat_nozeros %>% 
  mutate(labels = ifelse(feed>0.1|food>3000000, iso3c, NA))

consump_plot(chick_dat_nozeros, chick_dat_nozeros$food/1000000, chick_dat_nozeros$feed)
```

```{r}
chick_dat_sum<-chick_dat_sum %>% 
  mutate(labels = ifelse(feed>5000|food>1000000, iso3c, NA))

consump_plot(chick_dat_sum, chick_dat_sum$food/1000000, chick_dat_sum$feed/10000)
```

```{r}
cor.test(chick_dat$feed, chick_dat$food, type = "pearson")
cor.test(chick_dat_sum$feed, chick_dat_sum$food, type = "pearson")
```

# Chicken farm pressures vs food

```{r}
chick_dat<-chick_dat %>% 
  mutate(labels = ifelse(farm>0.5|food>3000000, iso3c, NA))

consump_plot(chick_dat, chick_dat$food/1000000, chick_dat$farm)

```
```{r}
chick_dat_nozeros<-chick_dat_nozeros %>% 
  mutate(labels = ifelse(farm>0.5|food>3000000, iso3c, NA))

consump_plot(chick_dat_nozeros, chick_dat_nozeros$food/1000000, chick_dat_nozeros$farm)

```

```{r}
chick_dat_sum<-chick_dat_sum %>% 
  mutate(labels = ifelse(farm>5000|food>1000000, iso3c, NA))

consump_plot(chick_dat_sum, chick_dat_sum$food/1000000, chick_dat_sum$farm/1000)
```

```{r}
cor.test(chick_dat$farm, chick_dat$food, type = "pearson")
cor.test(chick_dat_sum$farm, chick_dat_sum$food, type = "pearson")
```

# Chicken CHI vs food supply
Chicken

```{r}
chick_dat<-chick_dat %>% 
  mutate(labels = ifelse(total>0.5|food_supply>50, iso3c, NA))

consump_plot(chick_dat, chick_dat$food_supply, chick_dat$total)

```

```{r}
cor.test(chick_dat$total, chick_dat$food_supply, method = "pearson")
```
```{r}
chick_dat_nozeros<-chick_dat_nozeros %>% 
  mutate(labels = ifelse(total>0.5|food_supply>50, iso3c, NA))

consump_plot(chick_dat_nozeros, chick_dat_nozeros$food_supply, chick_dat_nozeros$total)

```

```{r}
chick_dat_sum<-chick_dat_sum %>% 
  mutate(labels = ifelse(total>5000|food_supply>50, iso3c, NA))

consump_plot(chick_dat_sum, chick_dat_sum$food_supply, chick_dat_sum$total/10000)

```

```{r}
cor.test(chick_dat_sum$total, chick_dat_sum$food_supply, type = "pearson")
```
# Chicken feed pressures vs food

```{r}
chick_dat<-chick_dat %>% 
  mutate(labels = ifelse(feed>0.1|food_supply>50, iso3c, NA))

consump_plot(chick_dat, chick_dat$food_supply, chick_dat$feed)

```

```{r}
chick_dat_nozeros<-chick_dat_nozeros %>% 
  mutate(labels = ifelse(feed>0.1|food_supply>50, iso3c, NA))

consump_plot(chick_dat_nozeros, chick_dat_nozeros$food_supply, chick_dat_nozeros$feed)

```

```{r}
chick_dat_sum<-chick_dat_sum %>% 
  mutate(labels = ifelse(feed>5000|food_supply>50, iso3c, NA))

consump_plot(chick_dat_sum, chick_dat_sum$food_supply, chick_dat_sum$feed/10000)

```

```{r}
cor.test(chick_dat$feed, chick_dat$food_supply, type = "pearson")
cor.test(chick_dat_sum$feed, chick_dat_sum$food_supply, type = "pearson")
```

# Chicken farm pressures vs food

```{r}
chick_dat<-chick_dat %>% 
  mutate(labels = ifelse(farm>0.5|food_supply>50, iso3c, NA))

consump_plot(chick_dat, chick_dat$food_supply, chick_dat$farm)

```
```{r}
chick_dat_nozeros<-chick_dat_nozeros %>% 
  mutate(labels = ifelse(farm>0.5|food_supply>50, iso3c, NA))

consump_plot(chick_dat_nozeros, chick_dat_nozeros$food_supply, chick_dat_nozeros$farm)

```

```{r}
chick_dat_sum<-chick_dat_sum %>% 
  mutate(labels = ifelse(farm>5000|food_supply>50, iso3c, NA))

consump_plot(chick_dat_sum, chick_dat_sum$food_supply, chick_dat_sum$farm/1000)
```

```{r}
cor.test(chick_dat$farm, chick_dat$food_supply, type = "pearson")
cor.test(chick_dat_sum$farm, chick_dat_sum$food_supply, type = "pearson")
```


# Salmon CHI vs food

```{r}
salmon_dat <- salmon_dat %>% 
  mutate(labels = ifelse(total>0.03|food>1000000, iso3c, NA))

consump_plot(salmon_dat, salmon_dat$food/1000000, salmon_dat$total)

```

```{r}
salmon_dat_nozeros <- salmon_dat_nozeros %>% 
  mutate(labels = ifelse(total>0.03|food>1000000, iso3c, NA))

consump_plot(salmon_dat_nozeros, salmon_dat_nozeros$food/1000000, salmon_dat_nozeros$total)

```

```{r}
salmon_dat_sum <- salmon_dat_sum %>% 
  mutate(labels = ifelse(total>300|food>200000, iso3c, NA))

consump_plot(salmon_dat_sum, salmon_dat_sum$food/100000, salmon_dat_sum$total/1000)

```

```{r}
cor.test(salmon_dat$total, salmon_dat$food, type = "pearson")
cor.test(salmon_dat_sum$total, salmon_dat_sum$food, type = "pearson")
```

# Salmon feed CHI vs. food 

```{r}
salmon_dat <- salmon_dat %>% 
  mutate(labels = ifelse(feed>0.03|food>200000, iso3c, NA))

consump_plot(salmon_dat, salmon_dat$food/1000000, salmon_dat$feed)

```
```{r}
salmon_dat_nozeros <- salmon_dat_nozeros %>% 
  mutate(labels = ifelse(feed>0.03|food>200000, iso3c, NA))

consump_plot(salmon_dat_nozeros, salmon_dat_nozeros$food/1000000, salmon_dat_nozeros$feed)

```

```{r}
salmon_dat_sum <- salmon_dat_sum %>% 
  mutate(labels = ifelse(feed>1000|food>20000, iso3c, NA))

consump_plot(salmon_dat_sum, salmon_dat_sum$food/100000, salmon_dat_sum$feed/1000)

```


```{r}
cor.test(salmon_dat$food, salmon_dat$feed, type = "pearson")
cor.test(salmon_dat_sum$food, salmon_dat_sum$feed, type = "pearson")
```
# Salmon farm CHI vs. food 

```{r}
salmon_dat <- salmon_dat %>% 
  mutate(labels = ifelse(farm>0.01|food>200000, iso3c, NA))

consump_plot(salmon_dat, salmon_dat$food/1000000, salmon_dat$farm)

```
```{r}
salmon_dat_nozeros <- salmon_dat_nozeros %>% 
  mutate(labels = ifelse(farm>0.01|food>200000, iso3c, NA))

consump_plot(salmon_dat_nozeros, salmon_dat_nozeros$food/1000000, salmon_dat_nozeros$farm)

```


```{r}
salmon_dat_sum <- salmon_dat_sum %>% 
  mutate(labels = ifelse(farm>50|food>200000, iso3c, NA))

consump_plot(salmon_dat_sum, salmon_dat_sum$food/100000, salmon_dat_sum$farm/100)

```

```{r}
cor.test(salmon_dat$food, salmon_dat$farm, type = "pearson")
cor.test(salmon_dat_sum$food, salmon_dat_sum$farm, type = "pearson")
```

# Salmon CHI vs. Food supply

```{r}
salmon_dat <- salmon_dat %>% 
  mutate(labels = ifelse(total>0.03|food_supply>5, iso3c, NA))

consump_plot(salmon_dat, salmon_dat$food_supply, salmon_dat$total)

```
```{r}
salmon_dat_nozeros <- salmon_dat_nozeros %>% 
  mutate(labels = ifelse(total>0.03|food_supply>5, iso3c, NA))

consump_plot(salmon_dat_nozeros, salmon_dat_nozeros$food_supply, salmon_dat_nozeros$total)

```

```{r}
salmon_dat_sum <- salmon_dat_sum %>% 
  mutate(labels = ifelse(total>300|food_supply>5, iso3c, NA))

consump_plot(salmon_dat_sum, salmon_dat_sum$food_supply, salmon_dat_sum$total/1000)

```

```{r}
cor.test(salmon_dat$total, salmon_dat$food_supply, type = "pearson")
cor.test(salmon_dat_sum$total, salmon_dat_sum$food_supply, type = "pearson")
```

# Salmon feed CHI vs. food 

```{r}
salmon_dat <- salmon_dat %>% 
  mutate(labels = ifelse(feed>0.03|food_supply>10, iso3c, NA))

consump_plot(salmon_dat, salmon_dat$food_supply, salmon_dat$feed)
```

```{r}
salmon_dat_nozeros <- salmon_dat_nozeros %>% 
  mutate(labels = ifelse(feed>0.03|food_supply>10, iso3c, NA))

consump_plot(salmon_dat_nozeros, salmon_dat_nozeros$food_supply, salmon_dat_nozeros$feed)
```


```{r}
salmon_dat_sum <- salmon_dat_sum %>% 
  mutate(labels = ifelse(feed>100|food_supply>10, iso3c, NA))

consump_plot(salmon_dat_sum, salmon_dat_sum$food_supply, salmon_dat_sum$feed/1000)

```


```{r}
cor.test(salmon_dat$food_supply, salmon_dat$feed, type = "pearson")
cor.test(salmon_dat_sum$food_supply, salmon_dat_sum$feed, type = "pearson")
```
# Salmon farm CHI vs. food 

```{r}
salmon_dat <- salmon_dat %>% 
  mutate(labels = ifelse(farm>0.01|food_supply>5, iso3c, NA))

consump_plot(salmon_dat, salmon_dat$food_supply, salmon_dat$farm)

```
```{r}
salmon_dat_nozeros <- salmon_dat_nozeros  %>% 
  mutate(labels = ifelse(farm>0.01|food_supply>5, iso3c, NA))

consump_plot(salmon_dat_nozeros , salmon_dat_nozeros $food_supply, salmon_dat_nozeros $farm)

```


```{r}
salmon_dat_sum <- salmon_dat_sum %>% 
  mutate(labels = ifelse(farm>50|food_supply>5, iso3c, NA))

consump_plot(salmon_dat_sum, salmon_dat_sum$food_supply, salmon_dat_sum$farm/100)
```

```{r}
cor.test(salmon_dat$farm, salmon_dat$food_supply, type = "pearson")
cor.test(salmon_dat_sum$food_supply, salmon_dat_sum$farm, type = "pearson")
```