---
title: "Juliette_crop_production"
author: "Juliette"
date: "5/22/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(readr)
library(tidyverse)
library(here)
library(countrycode)
library(doParallel)

prep <- "/home/shares/food-systems/Food_footprint/dataprep/"
final <- "/home/shares/food-systems/Food_footprint/final_data/" 
raw <- "/home/shares/food-systems/Food_footprint/_raw_data/" 

rgns_tif <- raster("/home/shares/food-systems/Food_footprint/dataprep/spatial/master_rgns.tif")
rgn_info <- read_csv(here("_spatial/output/master_rgns.csv"))

```



We will want to compare the crop production layers to FAO production.

1. Download 2016 FAO tonnes crop production data.

2. Convert crop names to MAPSPAM names (there is a conversion table for this)

3. Summarize by country and crop to get total tonnes

4. Get iso3c codes (no need to figure out the complex ones, some data can drop out for this...but do delete the China one, but keep mainland China)

5. For MAPSPAM maps, find the corrected 2016 production layers

6. Sum the 4 production types for each crop to get total production

7. For each crop do the following:
  - Sum the entire raster to get global production. Compare this to FAO global production.
  - Do a zonal sum using region raster to get the total production for each country. Compare this to the FAO global country values. This can be done with a scatterplot comparing the two sources of country production. And/or a histogoram of FAO_tonnes_production/MAPSPAM_corrected_tonnes_production.

8. Do a quick check to make sure that the raster with all crops matches the sum of the four production type rasters

**Note** pay special attention to MAPSPAM cateogires that combine different crops into a single category

Quick check to see how much of FAO production is covered in mapspam
# FAOSTAT production proportion
```{r}
# production_df <- read_csv(here("_analysis/checking_data/PE_data/FAOSTAT_2016_production.csv"))
# SPAM_sum <- production_df %>% 
#   filter(!`Item Code` %in% c(256, 257, 311, 656, 667, 826)) %>% # crops that aren't covered by MapSPAM and excluded from our study
#   summarize(sum(Value, na.rm = TRUE))
# FAO_sum <- production_df %>% 
#   summarize(sum(Value, na.rm = TRUE))
# # The proportion of SPAM production covered by FAOSTAT
# SPAM_sum / FAO_sum # 0.9906545 
```


Using FAO 2016 Data:

Grab and tidy FAO production data
```{r}

fao_prod_raw <- read_csv(file.path(raw, "FAO_data/v2020/FAO_crop_production/crops_FAOSTAT_data_5-22-2020.csv")) %>% 
  filter(Element == "Production")

names_table <- read_csv(here("crop_farm/data/MapSPAM_names.csv")) 
mapspam_names <- names_table  %>% 
  dplyr::select(SPAM_short_name, SPAM_full_name) %>% unique

##check out differences
setdiff(fao_prod_raw$Item, names_table$product_description_FAOSTAT) ## 61 names not matching up
setdiff(names_table$product_description_FAOSTAT, fao_prod_raw$Item) # 140 names not matching up
setdiff(names_table$item_code, fao_prod_raw$'Item Code') 
setdiff(fao_prod_raw$'Item Code', names_table$item_code) #257, 256, 311 (Oil palm, 	Palm kernels, kapokseed in shell)

table_short <- names_table %>% 
  dplyr::select(SPAM_short_name, SPAM_full_name, item_code) 

fao_prod <- fao_prod_raw %>% 
  rename(item_code = 'Item Code') %>% 
  left_join(table_short, by = "item_code")
## join isnt perfectly aligned
```


This join isn't perfect because mapspam separated out (millet, coffee)

```{r}
fao_country_total <- fao_prod %>% 
  group_by(Area, SPAM_full_name, SPAM_short_name) %>% 
  filter(Item != "Oil, palm") %>% 
  filter(Item != "Kapokseed in shell") %>% 
  filter(Item != "Palm kernels") %>%  ## mapspam doesnt map this so remove from our comparison
  dplyr::summarise(FAO_production= sum(Value, na.rm = TRUE)) %>% 
  mutate(iso3c = countrycode(Area, origin="country.name", destination = "iso3c")) %>% 
  rename(fao_country = Area) %>% 
  filter(fao_country != "China")

fao_global_total <- fao_prod %>% 
  filter(Item != "Oil, palm") %>% 
  filter(Item != "Kapokseed in shell") %>% 
  filter(Item != "Palm kernels") %>%  ## mapspam doesnt map this so remove from our comparison
  filter(Area != "China") %>% 
  group_by(SPAM_full_name, SPAM_short_name) %>% 
  dplyr::summarise(FAO_production= sum(Value, na.rm = TRUE)) 
```

## Grab and summarise total production from mapspam maps

```{r}

crops <- substring(list.files(file.path(prep, "crop_farm/scaled_maps_2016"), pattern = "A"), first = 6, last = 9)

global_production <- data.frame(SPAM_short_name = NA, SPAM_production = NA)
regional_production <- data.frame(ID_0 = NA, production = NA, iso3c = NA, Country = NA, SPAM_short_name = NA)

for(i in 1:length(crops)) {
  #crop_name = "maiz"

  ## prep the crop rasters
    crop_name <- crops[i]

    H <- raster(list.files(file.path(prep, "crop_farm/scaled_maps_2016"), pattern =  paste0(crop_name, "_H", sep = ""), full = TRUE))
    I <- raster(list.files(file.path(prep, "crop_farm/scaled_maps_2016"), pattern =  paste0(crop_name, "_I", sep = ""), full = TRUE))
    L <- raster(list.files(file.path(prep, "crop_farm/scaled_maps_2016"), pattern =  paste0(crop_name, "_L", sep = ""), full = TRUE))
    S <- raster(list.files(file.path(prep, "crop_farm/scaled_maps_2016"), pattern =  paste0(crop_name, "_S", sep = ""), full = TRUE))

    stack <- stack(H, I, L, S)
    raster_sum <- sum(stack, na.rm = TRUE)

    ## Global Total

     sum <- cellStats(raster_sum, "sum", na.rm=TRUE)
     crop_sum <- data.frame(SPAM_short_name = crop_name , SPAM_production = sum)
     global_production <- rbind(global_production, crop_sum)

    ## Region Total

      rgn_prod <- zonal(raster_sum, rgns_tif, fun="sum", progress="text", na.rm=TRUE)

      rgn_prod_df <- data.frame(rgn_prod) %>%
        rename(ID_0 = zone, production = sum) %>%
        left_join(rgn_info, by="ID_0") %>%
        mutate(SPAM_short_name = crop_name )

      regional_production <- rbind(regional_production, rgn_prod_df)

  }

```

Grab the raster that are _A and make sure that the totals are the same as summing all 4 subcategories

```{r}
crops <- substring(list.files(file.path(prep, "crop_farm/scaled_maps_2016"), pattern = "A"), first = 6, last = 9)

test_global_production <- data.frame(SPAM_short_name = NA, SPAM_production = NA)


for(i in 1:length(crops)) {
  #crop_name = "maiz"

  ## prep the crop rasters
    crop_name <- crops[i]

    raster <- raster(list.files(file.path(prep, "crop_farm/scaled_maps_2016"), pattern =  paste0(crop_name, "_A", sep = ""), full = TRUE))


    ## Global Total

     sum <- cellStats(raster, "sum", na.rm=TRUE)
     crop_sum <- data.frame(SPAM_short_name = crop_name , SPAM_production = sum)
     test_global_production <- rbind(test_global_production, crop_sum)

  }


differences <- test_global_production %>% 
  mutate(SPAM_production_A = SPAM_production) %>% 
  left_join(global_production) %>% 
  mutate(difference = SPAM_production_A - SPAM_production)

### checks out the sum of all 4 pieces are the same as the _A
```







Combine the FAO production data with our mapspam data

Global
```{r}
compare_global <- left_join(global_production, fao_global_total, by = "SPAM_short_name") %>% 
  mutate(per_diff = abs(SPAM_production-FAO_production)/((SPAM_production+FAO_production)/2),
         raw_diff = SPAM_production-FAO_production) %>% 
  dplyr::select(SPAM_full_name, SPAM_short_name,SPAM_production, FAO_production, per_diff, raw_diff )

write_csv(compare_global, here("_analysis/checking_data/JV_data/compare_total_production.csv"))
```

Regional
Check data check
```{r}
##quick check for rgns and crop matches
setdiff(regional_production$iso3c, fao_country_total$iso3c)
setdiff(fao_country_total$iso3c, regional_production$iso3c) ## All FAO rgns are in our regions

setdiff(regional_production$SPAM_short_name, fao_country_total$SPAM_short_name)
setdiff(fao_country_total$SPAM_short_name, regional_production$SPAM_short_name) ##no missing crops
```

Compare with FAO
```{r}

compare_rgn <- left_join(regional_production, fao_country_total, by = c("iso3c", "SPAM_short_name")) %>% 
  dplyr::select(iso3c, Country, SPAM_short_name, production, FAO_production) %>% 
  left_join(mapspam_names, by = "SPAM_short_name") %>% # some data in spam but not fao is missing 
  rename(SPAM_production = production) %>% 
   mutate(per_diff = abs(SPAM_production-FAO_production)/((SPAM_production+FAO_production)/2),
         raw_diff = SPAM_production-FAO_production)

write_csv(compare_rgn, here("_analysis/checking_data/JV_data/compare_rgn_production.csv"))
```

Looking at the countries and crops where mapspam reports prodcution and fao doesnt and vice versa

```{r}
summary(compare_rgn$FAO_production) # 5792  NAs
summary(compare_rgn$SPAM_production) # 1 NA (probably the NA row)

check_mapspam <- compare_rgn %>% 
  filter(SPAM_production == 0 & FAO_production > 0) %>% 
  filter(SPAM_full_name != "small millet") %>% 
  filter(SPAM_full_name != "pearl millet") %>% 
  filter(SPAM_full_name != "robusta coffee") %>% 
  filter(SPAM_full_name != "arabica coffee") 
 ## filter(FAO_production >= 100)
## 35 of our fruit fall into this category, and its not a completly insignificant amount of crops we are missing
## 108 of our rgns fall into this category


## check the totals of where spam == 0 and FAO_production >0

prop <- check_mapspam %>% 
  group_by(SPAM_full_name) %>% 
  mutate(total_missing_prod = sum(FAO_production)) %>% 
  ungroup() %>% 
  dplyr::select(-per_diff, -raw_diff) %>% 
  mutate(prop = FAO_production/total_missing_prod)
```
Number of crops that are "missing" for the top proportion countries
reunion = 18
comoros = 16
palestina = 21
samoa = 12
maldives = 12

## For each crop sum the global FAO production of these countries with no SPAM reported (but FAO reported) and then divide by the total global FAO production across all countries.  Hopefully, what we will see is that this FAO>0 and SPAM==0 is a very small proportion fo total produciton.

```{r}
global_missing <- check_mapspam %>% 
  group_by(SPAM_short_name, SPAM_full_name) %>% 
  dplyr::summarise(fao_production_noSPAM = sum(FAO_production))

compare <- global_production %>% 
  filter(!is.na(SPAM_short_name)) %>% 
  left_join(global_missing, by = "SPAM_short_name") %>% 
  mutate(fao_production_noSPAM = ifelse(is.na(fao_production_noSPAM), 0, fao_production_noSPAM),
         percent = fao_production_noSPAM/SPAM_production)
  
```



```{r}
check_fao_1 <- compare_rgn %>% 
  filter(SPAM_production > 0 & FAO_production == 0) %>% 
  filter(SPAM_full_name != "small millet") %>% 
  filter(SPAM_full_name != "pearl millet") %>% 
  filter(SPAM_full_name != "robusta coffee") %>% 
  filter(SPAM_full_name != "arabica coffee") %>% 
    filter(SPAM_production >= 100)
## south sudan producing a lot that FAO is missing
## 30 of our fruit fall into this category
## 50 of our rgns fall into this category

check_fao_2 <- compare_rgn %>% 
  filter(SPAM_production > 0 & is.na(FAO_production))
## 119 of our rgns fall into this category

```


Plot each crop: country comparison mapspam tonnes production: tonnes FAO production

```{r}
ggplot(compare_rgn) +
  geom_point(aes(x = SPAM_production, y = FAO_production, color = Country))+
  theme(legend.position = "none") +
  facet_wrap(~SPAM_full_name)
## its very hard to see specifics
```

```{r}
##create a single plot for each for easy viewing
path <- here("_analysis/checking_data/JV_data/crop_production_graphs/")

crop <- as.vector(unique(compare_rgn$SPAM_full_name))

 for(i in crop) {
  #crop_name = "maiz"  
  
  df <- compare_rgn %>% 
    filter(SPAM_full_name == i) 
  
  plot <-ggplot(df) +
    geom_point(aes(x = SPAM_production, y = FAO_production, color = Country))+
    ggtitle(i)+
    theme(legend.position = "none")
  
   ggsave(paste0(path, i, ".jpg", sep = ""), width=5, height=3, dpi=300)
    
  } 
  
```


```{r}
library(plotly)

test <- compare_rgn %>% 
  filter(SPAM_full_name == "sorghum")

test_plot <- ggplot(test) +
  geom_point(aes(x = SPAM_production, y = FAO_production, color = Country))+
  theme(legend.position = "none")

ggplotly(test_plot)
```



----


Using FAO 2010 Data:

Grab and tidy FAO production data
```{r}

fao_prod_raw_2010 <- read_csv(file.path(raw, "FAO_data/v2020/FAO_crop_production/crops_2010_FAOSTAT_data_5-26-2020.csv")) %>% 
  filter(Element == "Production")

names_table <- read_csv(here("crop_farm/data/MapSPAM_names.csv")) 

##check out differences
dplyr::setdiff(fao_prod_raw_2010$Item, names_table$product_description_FAOSTAT) ## 61 names not matching up
dplyr::setdiff(names_table$product_description_FAOSTAT, fao_prod_raw_2010$Item) # 140 names not matching up
setdiff(names_table$item_code, fao_prod_raw_2010$'Item Code') 
setdiff(fao_prod_raw_2010$'Item Code', names_table$item_code) #257, 256, 311 (Oil palm, 	Palm kernels, kapokseed in shell)

table_short <- names_table %>% 
  dplyr::select(SPAM_short_name, SPAM_full_name, item_code) 

fao_prod_2010 <- fao_prod_raw_2010 %>% 
   filter(Item != "Oil, palm") %>% 
  filter(Item != "Kapokseed in shell") %>% 
  filter(Item != "Palm kernels") %>%  ## mapspam doesnt map this so remove from our comparison
  filter(Area != "China") %>% 
  rename(item_code = 'Item Code') %>% 
  left_join(table_short, by = "item_code")
## join isnt perfectly aligned
```


This join isn't perfect because mapspam separated out (millet, coffee)

```{r}
fao_country_total_2010 <- fao_prod_2010 %>% 
  group_by(Area, SPAM_full_name, SPAM_short_name) %>% 
  dplyr::summarise(FAO_production= sum(Value, na.rm = TRUE)) %>% 
  mutate(iso3c = countrycode(Area, origin="country.name", destination = "iso3c")) %>% 
  rename(fao_country = Area) 

fao_global_total_2010 <- fao_prod_2010 %>% 
  group_by(SPAM_full_name, SPAM_short_name) %>% 
  dplyr::summarise(FAO_production= sum(Value, na.rm = TRUE)) 
```



Combine the FAO production data with our mapspam data

Global
```{r}
compare_global_2010 <- left_join(global_production, fao_global_total_2010, by = "SPAM_short_name") %>% 
  mutate(per_diff = abs(SPAM_production-FAO_production)/((SPAM_production+FAO_production)/2),
         raw_diff = SPAM_production-FAO_production) %>% 
  dplyr::select(SPAM_full_name, SPAM_short_name,SPAM_production, FAO_production, per_diff, raw_diff )

write_csv(compare_global_2010, here("_analysis/checking_data/JV_data/compare_total_production_2010.csv"))
```

Regional
Check data check
```{r}
##quick check for rgns and crop matches
setdiff(regional_production$iso3c, fao_country_total_2010$iso3c)
setdiff(fao_country_total_2010$iso3c, regional_production$iso3c) ## All FAO rgns are in our regions

setdiff(regional_production$SPAM_short_name, fao_country_total_2010$SPAM_short_name)
setdiff(fao_country_total_2010$SPAM_short_name, regional_production$SPAM_short_name) ##no missing crops
```

Compare with FAO
```{r}
compare_rgn_2010 <- left_join(regional_production, fao_country_total_2010, by = c("iso3c", "SPAM_short_name")) %>% 
  dplyr::select(iso3c, Country, SPAM_short_name, production, FAO_production) %>% 
  left_join(mapspam_names, by = "SPAM_short_name") %>% # some data in spam but not fao is missing 
  rename(SPAM_production = production) %>% 
   mutate(per_diff = abs(SPAM_production-FAO_production)/((SPAM_production+FAO_production)/2),
         raw_diff = SPAM_production-FAO_production)

write_csv(compare_rgn_2010, here("_analysis/checking_data/JV_data/compare_rgn_production_2010.csv"))
```

Looking at the countries and crops where mapspam reports prodcution and fao doesnt and vice versa

```{r}
summary(compare_rgn_2010$FAO_production) # 5792  NAs
summary(compare_rgn_2010$SPAM_production) # 1 NA (probably the NA row)

check_mapspam_2010 <- compare_rgn_2010 %>% 
  filter(SPAM_production == 0 & FAO_production > 0) %>% 
  filter(SPAM_full_name != "small millet") %>% 
  filter(SPAM_full_name != "pearl millet") %>% 
  filter(SPAM_full_name != "robusta coffee") %>% 
  filter(SPAM_full_name != "arabica coffee") 
 ## filter(FAO_production >= 100)
## 35 of our fruit fall into this category, and its not a completly insignificant amount of crops we are missing
## 108 of our rgns fall into this category

## check the totals of where spam == 0 and FAO_production >0

prop_2010 <- check_mapspam_2010 %>% 
  group_by(SPAM_full_name) %>% 
  mutate(total_missing_prod = sum(FAO_production)) %>% 
  ungroup() %>% 
  dplyr::select(-per_diff, -raw_diff) %>% 
  mutate(prop = FAO_production/total_missing_prod)
```
Number of crops that are "missing" for the top proportion countries
reunion = 18
comoros = 16
palestina = 21
samoa = 12
maldives = 12


```{r}
check_fao_1_10 <- compare_rgn_2010 %>% 
  filter(SPAM_production > 0 & FAO_production == 0) %>% 
  filter(SPAM_full_name != "small millet") %>% 
  filter(SPAM_full_name != "pearl millet") %>% 
  filter(SPAM_full_name != "robusta coffee") %>% 
  filter(SPAM_full_name != "arabica coffee") %>% 
    filter(SPAM_production >= 100)
## south sudan producing a lot that FAO is missing
## 30 of our fruit fall into this category
## 50 of our rgns fall into this category

check_fao_2_10 <- compare_rgn_2010 %>% 
  filter(SPAM_production > 0 & is.na(FAO_production))
## 119 of our rgns fall into this category

```


Plot each crop: country comparison mapspam tonnes production: tonnes FAO production

```{r}
ggplot(compare_rgn_2010) +
  geom_point(aes(x = SPAM_production, y = FAO_production, color = Country))+
  theme(legend.position = "none") +
  facet_wrap(~SPAM_full_name)
## its very hard to see specifics
```

```{r}
##create a single plot for each for easy viewing
path <- here("_analysis/checking_data/JV_data/crop_production_graphs_2010/")

crop <- as.vector(unique(compare_rgn_2010$SPAM_full_name))

 for(i in crop) {
  #crop_name = "maiz"  
  
  df <- compare_rgn_2010 %>% 
    filter(SPAM_full_name == i) 
  
  plot <-ggplot(df) +
    geom_point(aes(x = SPAM_production, y = FAO_production, color = Country))+
    ggtitle(i)+
    theme(legend.position = "none")+
    geom_abline(intercept=0, slope=1, color="red")
  
   ggsave(paste0(path, i, ".jpg", sep = ""), width=5, height=3, dpi=300)
    
  } 
  
```


```{r}
library(plotly)

test <- compare_rgn_2010 %>% 
  filter(SPAM_full_name == "sorghum")

test_plot <- ggplot(test) +
  geom_point(aes(x = SPAM_production, y = FAO_production, color = Country))+
  theme(legend.position = "none")

ggplotly(test_plot)
```

Comparing propotion missing from 2010 fao to 2016 fao
```{r}
prop_int <- prop_2010 %>% 
  rename(SPAM_production_2010 =SPAM_production,
         FAO_production_2010 = FAO_production,
         total_missing_prod_2010 = total_missing_prod,
         prop_2010 = prop)

prop_int_2 <- prop %>% 
  rename(SPAM_production_2016 =SPAM_production,
         FAO_production_2016 = FAO_production,
         total_missing_prod_2016 = total_missing_prod,
         prop_2016 = prop) 

prop_compare <- full_join(prop_int, prop_int_2)


setdiff(fao_prod_2010$Area, fao_prod$Area)
setdiff(fao_prod$Area, fao_prod_2010$Area)

setdiff(prop_int$iso3c, prop_int_2$iso3c)
setdiff(prop_int_2$iso3c, prop_int$iso3c)

```


create data frame that is mapspam scaled production, 2010 fao production and 2016 fao production. then do do 2 percent difs. should be a bigger differnce with 2010 than 2016 if scaled right
```{r}
compare_rgn_int <- compare_rgn %>% 
  dplyr::select(-raw_diff) %>% 
  rename(FAO_production_2016 = FAO_production,
         per_diff_2016 = per_diff)

compare_rgn_int_2 <- compare_rgn_2010%>% 
  dplyr::select(-raw_diff) %>% 
  rename(FAO_production_2010 = FAO_production,
         per_diff_2010 = per_diff)

compare_years <- left_join(compare_rgn_int, compare_rgn_int_2)

setdiff(compare_rgn_int$iso3c, compare_rgn_int_2$iso3c)
setdiff(compare_rgn_int_2$iso3c, compare_rgn_int$iso3c)

setdiff(compare_rgn_int$SPAM_full_name, compare_rgn_int_2$SPAM_full_name)
setdiff(compare_rgn_int_2$SPAM_full_name, compare_rgn_int$SPAM_full_name)

setdiff(compare_rgn_int$SPAM_production, compare_rgn_int_2$SPAM_production)
setdiff(compare_rgn_int_2$SPAM_production, compare_rgn_int$SPAM_production)

setdiff(compare_rgn_int$Country, compare_rgn_int_2$Country)
setdiff(compare_rgn_int_2$Country, compare_rgn_int$Country)


```


plot spam production vs fao 2010 and spam production fao 2010
```{r}

test_plot <- ggplot(compare_years) +
  geom_point(aes(x = SPAM_production, y = FAO_production_2016, color = SPAM_full_name), shape = 16)+
  geom_point(aes(x = SPAM_production, y = FAO_production_2010, color = SPAM_full_name), shape = 17) +
  labs(y= "FAO Production", x= "MapSPAM Production")
  
ggplotly(test_plot)
```

```{r}

path <- here("_analysis/checking_data/JV_data/compare_years_production_graphs/")
crop <- as.vector(unique(compare_years$SPAM_full_name))

 for(i in crop) {
  #crop_name = "maiz"  
  
  df <- compare_years %>% 
    filter(SPAM_full_name == i) 
  
  plot <- ggplot(df) +
  geom_point(aes(x = SPAM_production, y = FAO_production_2016, color = Country), shape = 16)+ ## circle
  geom_point(aes(x = SPAM_production, y = FAO_production_2010, color = Country), shape = 17) + ## triangle
  ggtitle(i)+
  labs(y= "FAO Production", x= "MapSPAM Production") +
  theme(legend.position = "none")+
    geom_abline(intercept=0, slope=1, color="red")
  
   ggsave(paste0(path, i, ".jpg", sep = ""), width=5, height=3, dpi=300)
    
  } 
```



plot percent differnet 2010 vs 2016
```{r}

path <- here("_analysis/checking_data/JV_data/percent_difference/")
crop <- as.vector(unique(compare_years$SPAM_full_name))

 for(i in crop) {
  #crop_name = "maiz"  
  
  df <- compare_years %>% 
    filter(SPAM_full_name == i) 
  
  plot <- ggplot(df) +
  geom_point(aes(x = per_diff_2016, y = per_diff_2010, color = Country))+ 
  geom_point(aes(x = SPAM_production, y = FAO_production_2010, color = Country)) + 
  ggtitle(i)+
  labs(y= "Percent Difference spam fao 2010", x= "Percent Difference spam fao 2016") +
  theme(legend.position = "none")+
    geom_abline(intercept=0, slope=1, color="red")
  
   ggsave(paste0(path, i, ".jpg", sep = ""), width=5, height=3, dpi=300)
    
  } 
```





































