---
title: "Untitled"
author: "Caitie"
date: "21/08/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
```

# Production

```{r}
chicken_prod<-read.csv(here("_analysis/data/broiler_production.csv"))
salmon_prod<-read.csv(here("_analysis/data/salmon_production.csv"))
```

```{r}
total_chicken<-sum(chicken_prod$broiler_carcass_wt_tonnes)

chicken_prod<-chicken_prod %>% 
  mutate(prop = broiler_carcass_wt_tonnes/total_chicken)

high_cpi_prod_c<-chicken_prod %>% 
  filter(iso3c %in% c("USA", "BRA", "CHN", "ARG", "IDN"))
```

```{r}
total_salmon<-2413786

salmon_prod<-salmon_prod %>% 
  mutate(prop = fao_tonnes_production/total_salmon)

high_cpi_prod_s<-salmon_prod %>% 
  filter(iso3c %in% c("NOR", "ISL", "CHL", "GBR", "CAN"))
```

# Global summary of chicken and salmon

Land and EEZ combined
```{r}
global<-read.csv(here("_analysis/data/zonal_extract/average_rescaled_pressures_combined_eez_land_global.csv"))

global_chicken_salmon<- global %>% 
  group_by(animal_system) %>% 
  summarise(total = sum(value, na.rm = T))

global_chicken_salmon

global_chicken_salmon[1,2]/global_chicken_salmon[2,2]
```

Land and all ocean

```{r}
all<-read.csv(here("_analysis/data/zonal_extract/average_rescaled_pressures_all_global.csv"))
```


# Country summary of chicken and salmon

High pressures cells

```{r}
cell_count<-read.csv(here("_analysis/figures/overlap_map/data/cell_count.csv"))
```

```{r}
high_chicken<- cell_count %>% 
   filter(category %in% as.factor(c("high chicken\nzero salmon", "high chicken\nmedium salmon", "high chicken\nlow salmon", "high chicken\nhigh salmon"))) 

sum(high_chicken$prop_cells, na.rm = T)
```

```{r}
high_salmon<- cell_count %>% 
   filter(category %in% as.factor(c("zero chicken\nhigh salmon", "low chicken\nhigh salmon", "medium chicken\nhigh salmon", "high chicken\nhigh salmon"))) 

sum(high_salmon$prop_cells, na.rm = T)
```

Average country and EEZ

```{r}
country_average<-read.csv(here("_analysis/data/zonal_extract/average_rescaled_pressures_country.csv"))
```

```{r}
country_chicken<- country_average %>% 
  filter(animal_system == "broiler") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total))

country_chicken
```

```{r}
country_salmon<- country_average %>% 
  filter(animal_system == "salmon") %>% 
  group_by(iso3c, Country) %>% 
  summarise(total = sum(value, na.rm = T)) %>% 
  arrange(desc(total))

country_salmon
```
# Overlap summary of chicken and salmon

Total footprint

```{r}
total_footprint<-cell_count %>% 
  filter(!category %in% as.factor(c("zero chicken\nzero salmon")))

sum(total_footprint$prop_cells, na.rm = T)

```

Chicken footprint
```{r}
total_footprint_chicken<-cell_count %>% 
  filter(!category %in% as.factor(c("zero chicken\nzero salmon", "zero chicken\nlow salmon", "zero chicken\nmedium salmon", "zero chicken\nhigh salmon")))

sum(total_footprint_chicken$prop_cells, na.rm = T)
```
Salmon footprint
```{r}
total_footprint_salmon<-cell_count %>% 
  filter(!category %in% as.factor(c("zero chicken\nzero salmon", "low chicken\nzero salmon", "medium chicken\nzero salmon", "high chicken\nzero salmon")))

sum(total_footprint_salmon$prop_cells, na.rm = T)
```
Amount of overlap

```{r}
overlap<-cell_count %>% 
  filter(!category %in% c("zero chicken\nzero salmon", "high chicken\nzero salmon", "medium chicken\nzero salmon", "low chicken\nzero salmon", "zero chicken\nlow salmon","zero chicken\nmedium salmon","zero chicken\nhigh salmon"))

overlap2<-cell_count %>% 
  filter(!category %in% c("zero chicken\nzero salmon"))

sum(overlap$prop_cells)
sum(cell_count$prop_cells)

sum(overlap$number_cells)/((sum(total_footprint_chicken$number_cells) + sum(total_footprint_salmon$number_cells)))

```

Greatest overlap

```{r}
overlap %>% 
  arrange(desc(prop_cells))
```
# Land vs. sea footprint

```{r}
land_sea<-read.csv(here("_analysis/data/zonal_extract/average_rescaled_pressures_global.csv"))

land_sea_animal<- land_sea %>% 
  group_by(animal_system, location) %>% 
  summarise(total = sum(value, na.rm = T))

land_sea_animal
```

Entire ocean

```{r}
ocean<-read.csv(here("_analysis/data/zonal_extract/average_rescaled_pressures_ocean_global.csv")) %>% 
  group_by(animal_system) %>% 
  summarise(total = sum(value, na.rm = T))

ocean
```


# Feed/on-farm summary of chicken and salmon

```{r}
global_feed<-global %>% 
    filter(!source == "farm") %>% #,
#           animal_system == "salmon") %>% 
  group_by(animal_system, source, subsource, stressor) %>% 
  summarise(total = sum(value, na.rm = T))

global_farm<-global %>% 
    filter(!source == "feed") %>% 
  group_by(animal_system,source, stressor) %>% 
  summarise(total = sum(value, na.rm = T))

global_feed

#Chicken proportion feed
global_feed[2,3]/(global_feed[2,3]+global_feed[1,3])

# Salmon proportion feed
global_feed[4,3]/(global_feed[3,3]+global_feed[4,3])

#Chicken feed vs. salmon feed
global_feed[2,3]/global_feed[4,3]

#Chicken farm vs. salmon farm
global_feed[1,3]/global_feed[3,3]

#Salmon feed vs. farm
global_feed[4,3]/global_feed[3,3]

# Chicken farm vs. feed
global_feed[1,3]/global_feed[2,3]


```

```{r}
global_feed_source<-global %>% 
  filter(!source == "farm") %>% 
  group_by(animal_system, subsource) %>% 
  summarise(total = sum(value, na.rm = T))

global_feed_source

# Salmon source

global_feed_source[4,3]/(global_feed_source[3,3]+global_feed_source[4,3])

# Chicken source
global_feed_source[1,3]/(global_feed_source[1,3]+global_feed_source[2,3])
```

# Dominant pressures chicken vs salmon

```{r}
dom_chicken<-read.csv(here("_analysis/figures/dominant_pressure_map/chicken_dominant_pressure.csv")) %>% 
  filter(!is.na(max_val) == T)

length(which(dom_chicken$cat == "disturbance"))/nrow(dom_chicken)
length(which(dom_chicken$cat == "ghg"))/nrow(dom_chicken)
length(which(dom_chicken$cat == "nutrients"))/nrow(dom_chicken)
length(which(dom_chicken$cat == "water"))/nrow(dom_chicken)

```

```{r}
dom_salmon<-read.csv(here("_analysis/figures/dominant_pressure_map/salmon_dominant_pressure.csv"))%>% 
  filter(!is.na(max_val) == T)

length(which(dom_salmon$cat == "disturbance"))/nrow(dom_salmon)
length(which(dom_salmon$cat == "ghg"))/nrow(dom_salmon)
length(which(dom_salmon$cat == "nutrients"))/nrow(dom_salmon)
length(which(dom_salmon$cat == "water"))/nrow(dom_salmon)
```

```{r}
global_stress<- global %>% 
  group_by(animal_system, stressor, ) %>% 
  summarise(total = sum(value, na.rm = T))

land_sea_stress<- land_sea %>% 
  group_by(animal_system, stressor, location) %>% 
  summarise(total = sum(value, na.rm = T))

land_sea_stress

marine_stress<-land_sea_stress %>% 
  filter(location == "marine",
         animal_system == "salmon")

marine_stress %>% 
  mutate(prop = total/sum(marine_stress$total))
```

