---
title: "summed_stressor"
author: "Juliette"
date: "4/20/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This markdown calculates rasters for 

1. sum of each stressor by system (saved on Aurora: stressor_summary/equal_area/system_stressor)
2. sum of each stressor across all systems (saved on Aurora: stressor_summary/equal_area/stressor)
3. sum of all rescaled pressure rasters (i.e., cumulative pressure)

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```



# sum each pressure for each food system

```{r}
# function

system_sum <- function(system){ #system="salmon"

stressor_list <- c("ghg", "water", "nutrient", "disturbance")
system_search <- paste0("_", system, "_")
for(stressor in stressor_list){
#stressor <- "ghg"
stressor_files <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell", 
           pattern=stressor,
           full=TRUE)
stressor_files <- grep(system_search, stressor_files, value=TRUE)

stressor_stack <- stack(stressor_files)
stressor_sum <- sum(stressor_stack, na.rm=TRUE)
#plot(log(stressor_sum + 1))
writeRaster(stressor_sum, sprintf("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/%s_%s_per_cell.tif", system, stressor), overwrite=TRUE)
}
}
```

```{r}

system_sum(system="chickens")
system_sum(system="salmon")

plot(raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/chickens_ghg_per_cell.tif"))

```

# sum each pressure for both food systems
For each stressor get sum of all inputs across all systems.
```{r}

stressor_list <- c("ghg", "water", "nutrient", "disturbance")

for(stressor in stressor_list){
#stressor <- "ghg"
  
  stressor_files <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell", pattern=stressor,
           full=TRUE)

stressor_stack <- stack(stressor_files)
stressor_sum <- sum(stressor_stack, na.rm=TRUE)
#plot(log(stressor_sum + 1))
writeRaster(stressor_sum, sprintf("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/stressor/%s_per_cell.tif", 
                                  stressor), 
            overwrite=TRUE)
}

```

# chi
Sum all rescaled stressor files to get cumulative pressure.
```{r}

pressure_files <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell_rescaled", pattern="rescaled", full=TRUE)

chi_stack <- stack(pressure_files)
chi <- sum(chi_stack, na.rm=TRUE)
writeRaster(chi, "/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/cumulative_stress.tif", overwrite=TRUE)

check <- raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/cumulative_stress.tif")
cellStats(check, "sum", na.rm=TRUE) # should be 4 x 1000000


```

# proportion of total chi for each food system/stressor
cumulative pressure for each of: chicken and salmon.

```{r}

chi_rescale <- read_csv(here("_analysis/rescale_values.csv"))

## function
rescale_food_system <- function(chi_rescale, food_system="chickens"){
  
for(stressor in chi_rescale$pressure){ #stressor = "ghg"

stressor_system_file <- raster(sprintf("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/%s_%s_per_cell.tif", food_system, stressor))

resc_num <- chi_rescale$global_total[chi_rescale$pressure==stressor]

rescaled_raster = raster::calc(stressor_system_file, fun=function(x){ifelse(x>0, 
                                       (x/resc_num)*1000000, 
                                       0)})
#plot(rescaled_raster)
writeRaster(rescaled_raster, sprintf("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/system_stressor/%s_%s_rescaled.tif", food_system, stressor), overwrite=TRUE)
}
}


rescale_food_system(chi_rescale, food_system="chickens")
rescale_food_system(chi_rescale, food_system="salmon")

check <- raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/system_stressor/salmon_ghg_rescaled.tif")
check
cellStats(check, sum, na.rm=TRUE)
```

## Get cumulative for chickens and salmon
```{r}

broilers <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/system_stressor", pattern="chickens", full=TRUE)
broilers_stack <- stack(broilers)
broilers_chi <- sum(broilers_stack, na.rm=TRUE)
writeRaster(broilers_chi, "/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/chickens_cumulative_stress.tif", overwrite=TRUE)

salmon <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/system_stressor", pattern="salmon", full=TRUE)
salmon_stack <- stack(salmon)
salmon_chi <- sum(salmon_stack, na.rm=TRUE)
writeRaster(salmon_chi, "/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/salmon_cumulative_stress.tif", overwrite=TRUE)
plot(salmon_chi)
```

#quick checks
```{r}
cum <- raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/cumulative_stress.tif")
cellStats(cum, "sum", na.rm=TRUE) # should equal 4


salmon <- raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/salmon_cumulative_stress.tif")
broiler <- raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/chickens_cumulative_stress.tif")

total <- salmon+broiler
cellStats(total, "sum", na.rm=TRUE)
```