---
title: "Scaling values"
output: html_document
editor_options: 
  chunk_output_type: console
---

Scaling is based on the global total of each pressure due to chicken and salmon production.

Here I will calculate the total global total of each pressure.  This will be saved as a csv file and used in subsequent scripts to rescale the rasters.

I use the original lat/long coordinate reference system rasters because these values are the least manipulated and should be the most accurate (although this really will not make a difference).


```{r setup, include=FALSE}
library(rgdal)
library(sp)
library(raster)
library(tidyverse)
library(here)
```

```{r}
pressure_list <- c("ghg", "nutrient", "disturbance", "water")

rescale_data <- data.frame(pressure = pressure_list, global_total = NA)

for(pressure in pressure_list){ # pressure = "water"
food_files_pressure <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/raw", full=TRUE, pattern = pressure)
# farm first:

stack_pressure <- stack(food_files_pressure)

total_pressure <- raster::calc(stack_pressure, fun=sum, na.rm=TRUE, progress="text")

sum_stressor <- cellStats(total_pressure, stat='sum', na.rm=TRUE)
rescale_data$global_total[rescale_data$pressure == pressure] <- sum_stressor

}
write_csv(rescale_data, here("_analysis/rescale_values.csv"))

raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw/farm_land_chickens_industrial_meat_ghg.tif")
raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw/farm_marine_salmon_aquaculture_meat_ghg.tif")
```


# rescaled for each food system/stressor/feed
scaling each summed chicken and salmon stressor raster relative to global total stress of both food systems combined.

```{r}


chi_rescale <- read_csv(here("_analysis/rescale_values.csv"))

## function

for(stressor in chi_rescale$pressure){ #stressor = "nutrient"

stressor_system_files <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell", pattern=stressor, full=TRUE)
file_names <- basename(stressor_system_files)
file_names <- gsub("_per_cell.tif", "", file_names)
file_names <- paste0(file_names, "_rescaled.tif")
stressor_system_stack <- stack(stressor_system_files)

resc_num <- chi_rescale$global_total[chi_rescale$pressure==stressor]

rescaled_raster_stack = raster::calc(stressor_system_stack, fun=function(x){ifelse(x>0, 
                                      (x/resc_num) * 1000000, 
                                       0)})
names(stressor_system_stack) <- file_names

for(i in 1:length(file_names)) { # i=1
  single_band <- raster(rescaled_raster_stack, layer = i)
  
writeRaster(single_band, sprintf("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell_rescaled/%s", names(single_band)),
              overwrite=TRUE)

}
}
raster("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell_rescaled/gall_peter_feedcrop_land_chickens_industrial_meat_ghg_rescaled.tif")
raster("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell_rescaled/gall_peter_feedcrop_marine_salmon_aquaculture_meat_ghg_rescaled.tif")

```

