---
title: "Transfer file script"
output: html_document
editor_options: 
  chunk_output_type: console
---
Copying the relevant data from the food systems location to the chicken/salmon folder.
```{r setup, include=FALSE}

library(tidyverse)

```

Copy the original raw data layer files over. We only need the broiler and salmon aquaculture ones, but I am moving everything over in case we find we need something extra.

```{r}
from <- list.files("/home/shares/food-systems/Food_footprint/all_food_systems/datalayers", pattern=".tif", full=TRUE)
to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/datalayers"

file.copy(from, to)
```

Next copy over the relevant "raw" data files. These are not the rawest data, despite being in a folder called "raw". They have been manipulated to combine feed category pressures.  But this is the raw resolution of the data.

```{r}

from_raw <- list.files("/home/shares/food-systems/Food_footprint/all_food_systems/analysis/raw", full=TRUE)
from_raw_list <- grep("chickens_industrial_meat|salmon_aquaculture", from_raw, value=TRUE)

to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/raw"

file.copy(from_raw_list, to)


```


These are the rasters projected to mollweide. These are used for rescaling and visualization because they are equal area.
```{r}
from_mol <- list.files("/home/shares/food-systems/Food_footprint/all_food_systems/analysis/_tif_equal_area_proj_per_cell", full=TRUE)

from_mol_list <- grep("chickens_industrial_meat|salmon_aquaculture", from_mol, value=TRUE)

to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell"

file.copy(from_mol_list, to)


```

Feed revision

The following is a change in the way we calculate fofm feed.
For the food project we used the estimated tonnes of forage fish consumption for each food group from Halley's paper: "Avoiding the ecological limits of forage fish for fed aquaculture". She estimated about 2.8 million tonnes of forage fish taxa are fed to salmon.  Here, we estimate consumption using the following formula:

feed conversion rate x proportion of fofm in diet x tonnes salmon production = tonnes of fish oil fish meal

To convert from fish oil/meal to live weight fish we use assume a loss of 72% (i.e., we divide fofm by 0.28).

Based on these measurements, we estimate about 2,493,129 tonnes of consumption by salmon. We assume a globally consistent diet and fcr, so we can simply convert our estimates by multiplying the salmon fofm pressures by 0.886 (i.e., 2,493,129 / 2,813,893).

NOTE: no changes were made to the files transferred to datalayers (I think those are there as backup/archive, and we don't do anything with them)

This is mostly here for record keeping.
```{r}

# first copy over the originals to a new file, the ones in the raw folder will be overwritten

from <-  list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/raw", pattern="feedfofm_marine_salmon_aquaculture", full=TRUE)
to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/salmon_fofm_feed_unaltered"

file.copy(from, to)

from <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell", pattern = "feedfofm_marine_salmon", full=TRUE)
to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/salmon_fofm_feed_unaltered"
file.copy(from, to)


feed_change_raw <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/salmon_fofm_feed_unaltered", full=TRUE)
feed_change_raw <- grep(x=feed_change_raw, pattern="gall_peter", value=TRUE, invert=TRUE)

for(file in feed_change_raw){ # file = feed_change_raw[1]
  tmp <- raster::raster(file)
  name <- basename(file)
  start <- raster::cellStats(tmp, "sum", na.rm=TRUE)
  new_tmp <- tmp*0.886
  end <- raster::cellStats(new_tmp, "sum", na.rm=TRUE)
  start
  end
  cat(end/start)
  raster::writeRaster(new_tmp, sprintf("/home/shares/food-systems/Food_footprint/chicken_salmon/raw/%s", name), overwrite=TRUE)
}

feed_change_gp <- list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/salmon_fofm_feed_unaltered", full=TRUE)
feed_change_gp <- grep(x=feed_change_gp, pattern="gall_peter", value=TRUE)

for(file in feed_change_gp){ # file = feed_change_gp[1]
  tmp <- raster::raster(file)
  name <- basename(file)
  start <- raster::cellStats(tmp, "sum", na.rm=TRUE)
  new_tmp <- tmp*0.886
  end <- raster::cellStats(new_tmp, "sum", na.rm=TRUE)
  start
  end
  cat(end/start)
  raster::writeRaster(new_tmp, sprintf("/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell/%s", name), overwrite=TRUE)
}



```



These are the spatial layers I need for summarizing

```{r}

from_spatial <- list.files("/home/kuempel/food_chicken_salmon/_spatial/output", full=TRUE)
from_spatial_list <- from_spatial[c(1,4,8)]

from_spatial2<-list.files("/home/kuempel/food_chicken_salmon/_spatial", full = TRUE)

to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/_spatial"

file.copy(from_spatial_list, to)

```



```{r}
prod_files <- c("/home/kuempel/food_chicken_salmon/_analysis/data/broiler_production.csv", "/home/kuempel/food_chicken_salmon/_analysis/data/salmon_production.csv")

to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/production"

file.copy(prod_files, to)
```

```{r}

tmp <- raster::stack(list.files("/home/shares/food-systems/Food_footprint/chicken_salmon/raw", 
                 full=TRUE))

total <- raster::cellStats(tmp, "sum", na.rm=TRUE)
total <- as.data.frame(total) 
total <- cbind(total, names=row.names(total))
  mutate(names = row.names(total))

write_csv(total, here("checking_cs.csv"))
                 
```