---
title: "Transfer file script"
output: html_document
editor_options: 
  chunk_output_type: console
---
Copying the relevant data from the food systems location to the chicken/salmon folder.
```{r setup, include=FALSE}

library(tidyverse)

```

Copy the original raw data layer files over. We only need the broiler and salmon aquaculture ones, but I am moving everything over in case we find we need something extra.

```{r}
from <- list.files("/home/shares/food-systems/Food_footprint/all_food_systems/datalayers", pattern=".tif", full=TRUE)
to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/datalayers"

file.copy(from, to)
```

Next copy over the relevant "raw" data files. These are not the rawest data, despite being in a folder called "raw". They have been manipulated to combine feed category pressures.  But this is the raw resolution of the data.

```{r}

from_raw <- list.files("/home/shares/food-systems/Food_footprint/all_food_systems/analysis/raw", full=TRUE)
from_raw_list <- grep("chickens_industrial_meat|salmon_aquaculture", from_raw, value=TRUE)

to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/raw"

file.copy(from_raw_list, to)

```


These are the rasters projected to mollweide. These are used for rescaling and visualization because they are equal area.
```{r}
from_mol <- list.files("/home/shares/food-systems/Food_footprint/all_food_systems/analysis/_tif_equal_area_proj_per_cell", full=TRUE)

from_mol_list <- grep("chickens_industrial_meat|salmon_aquaculture", from_mol, value=TRUE)

to <- "/home/shares/food-systems/Food_footprint/chicken_salmon/_tif_equal_area_proj_per_cell"

file.copy(from_mol_list, to)

```