---
title: "Untitled"
author: "Caitie"
date: "14/07/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)

options(scipen = 999)
```

# Load raw data

This is the raw data in native units for each stressor - stressors cannot be added together

```{r}
raw<-read.csv(here("_analysis", "data", "zonal_extract", "sum_pressures_country.csv")) # Raw values
```


# Total stressors

```{r}
raw %>% 
  group_by(stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

stressors<-raw %>% 
  group_by(stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))
```

## Total stressors by system

```{r}
raw %>% 
  group_by(animal_system, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

system_stressor<-raw %>% 
  group_by(animal_system, stressor) %>% 
  summarise(system_stress = sum(value, na.rm = T)) %>% 
  left_join(.,stressors, by = "stressor") %>% 
  mutate(prop = system_stress/total_stress)
```

## Total stressors by locatoin
```{r}
raw %>% 
  group_by(location, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

location_stressor<-raw %>% 
  group_by(location, stressor) %>% 
  summarise(location_stress = sum(value, na.rm = T)) %>% 
  left_join(.,stressors, by = "stressor") %>% 
  mutate(prop = location_stress/total_stress)
```

## Total stressors by source
```{r}
raw %>% 
  group_by(source, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

source_stressor<-raw %>% 
  group_by(source, stressor) %>% 
  summarise(source_stress = sum(value, na.rm = T)) %>% 
  left_join(.,stressors, by = "stressor") %>% 
  mutate(prop = source_stress/total_stress)
```

## Total stressors by subsource
```{r}
raw %>% 
  filter(!source == "farm") %>% 
  group_by(subsource, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

subsource_stressor<-raw %>% 
  filter(!source == "farm") %>% 
  group_by(subsource, source, stressor) %>% 
  summarise(subsource_stress = sum(value, na.rm = T)) %>% 
  left_join(.,source_stressor, by = c("stressor", "source")) %>% 
  mutate(prop = subsource_stress/source_stress)
```

## Total stressors by location and source
```{r}
raw %>% 
  group_by(location, source, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

loc_source_stressor<-raw %>% 
  group_by(location, source, stressor) %>% 
  summarise(loc_source_stress = sum(value, na.rm = T)) %>% 
  left_join(.,location_stressor, by = c("stressor", "location")) %>% 
  mutate(prop = loc_source_stress/location_stress)
```

## Total stressor by animal system and source
```{r}
raw %>% 
  group_by(animal_system, source, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

an_source_stressor<-raw %>% 
  group_by(animal_system, source, stressor) %>% 
  summarise(an_source_stress = sum(value, na.rm = T)) %>% 
  left_join(.,system_stressor, by = c("stressor", "animal_system")) %>% 
  mutate(prop = an_source_stress/system_stress)
```

## Total stressor by animal system and location
```{r}
raw %>% 
  group_by(animal_system, location, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

an_location_stressor<-raw %>% 
  group_by(animal_system, location, stressor) %>% 
  summarise(an_loc_stress = sum(value, na.rm = T)) %>% 
  left_join(.,system_stressor, by = c("stressor", "animal_system")) %>% 
  mutate(prop = an_loc_stress/system_stress)
```
# Total stressors by country

```{r}
raw %>% 
  group_by(iso3c, Country, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

country_stressors<-raw %>% 
  group_by(iso3c, Country, stressor) %>% 
  summarise(country_stress = sum(value, na.rm = T)) %>% 
  left_join(., stressors, by = c("stressor")) %>% 
  mutate(prop = country_stress/total_stress)
```

## By country and system

```{r}
raw %>% 
  group_by(iso3c, Country, animal_system, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

country_system_stressors<-raw %>% 
  group_by(iso3c, Country, animal_system, stressor) %>% 
  summarise(country_system_stress = sum(value, na.rm = T)) %>% 
  left_join(., country_stressors, by = c("iso3c", "Country", "stressor")) %>% 
  mutate(prop = country_system_stress/country_stress)
```

GHG

```{r}
ghg_country_system_stressors<-country_system_stressors %>% 
  filter(stressor == "ghg",
         animal_system == "salmon")
```


Water

```{r}
water_country_system_stressors<-country_system_stressors %>% 
  filter(stressor == "water",
         animal_system == "broiler")
```

Disturbance

```{r}
disturb_country_system_stressors<-country_system_stressors %>% 
  filter(stressor == "disturbance",
         animal_system == "broiler")
```

Nutrient

```{r}
nutri_country_system_stressors<-country_system_stressors %>% 
  filter(stressor == "nutrient",
         animal_system == "broiler")
```
# Total stressors by land vs sea

```{r}
raw %>% 
  group_by(location, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

land_sea<-raw %>% 
  group_by(location, stressor) %>% 
  summarise(location_stress = sum(value, na.rm = T)) %>% 
  left_join(., stressors, by = "stressor") %>% 
  mutate(prop = location_stress/total_stress)
```

```{r}
raw %>% 
  group_by(iso3c, Country,location, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))
```
# Total stressors by feed vs. farm

```{r}
raw %>% 
  group_by(source, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

feed_farm<-raw %>% 
  group_by(source, stressor) %>% 
  summarise(source_stress = sum(value, na.rm = T)) %>% 
  left_join(., stressors, by = "stressor") %>% 
  mutate(prop = source_stress/total_stress)
```

```{r}
raw %>% 
  group_by(location, source, stressor) %>% 
  summarise(total_stress = sum(value, na.rm = T))

feed_farm_location<-raw %>% 
  group_by(location, source, stressor) %>% 
  summarise(source_stress = sum(value, na.rm = T)) %>% 
  left_join(., land_sea, by = c("location", "stressor")) %>% 
  mutate(prop = source_stress/location_stress)
```

# Production data

## Chicken production

FAO reports carcass wt 
```{r}
broiler_prod<-read.csv(here("_analysis/data/broiler_production.csv"))
```

