---
title: "aligning_EEZ"
author: "Juliette"
date: "4/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This markdown aligns EEZs to our region list.


```{r}
library(tidyverse)
library(dplyr)
library(raster)
library(rgdal)
library(sf)
library(fasterize)
library(readr)
library(here)
library(mapview)
library(countrycode)

prep <- "/home/shares/food-systems/Food_footprint/dataprep/"
food_crs <- "+proj=longlat +datum=WGS84 +ellps=WGS84 +towgs84=0,0,0"
food_raster <- raster(nrows=2160, ncols=4320, xmn=-180, xmx=180, ymn=-90, ymx=90)
  
master_rgns <- read_csv(here("_spatial/output/master_rgns.csv"))

EEZ_start <- st_read("/home/shares/food-systems/Food_footprint/_raw_data/marine_regions/Intersect_EEZ_IHO_v4_2020/Intersect_EEZ_IHO_v4_2020.shp")

```

## EEZ raster 

Make a few small changes to the downloaded EEZ map to match our region resolution.

We assigned territorial EEZs without an ISO3 code to their administrative country.

```{r}

EEZ_shape <- EEZ_start %>%
  mutate(ISO_TER1 = as.character(ISO_TER1)) %>%
    mutate(ISO_SOV1 = as.character(ISO_SOV1))

# Regions from the master list that are not in EEZ file
no_eez <- setdiff(master_rgns$iso3c, EEZ_shape$ISO_TER1)
landlocked <- read_csv(here("_spatial/output/UNSD_Methodology.csv")) %>%
  filter(Land_Locked == "x") 
setdiff(no_eez, landlocked$iso3c)

## British Indian Ocean Territory
EEZ_shape$ISO_TER1[EEZ_shape$MARREGION== "Chagos Archipelago part of the Indian Ocean"] <- "IOT"  
## Madeira Island
EEZ_shape$ISO_TER1[EEZ_shape$MARREGION== "Portuguese (Madeira) part of the North Atlantic Ocean"] <- "XMI"  

# Check again
# Regions from the master list that are not in EEZ file
no_eez <- setdiff(master_rgns$iso3c, EEZ_shape$ISO_TER1)
landlocked <- read_csv(here("_spatial/output/UNSD_Methodology.csv")) %>%
  filter(Land_Locked == "x") 
setdiff(no_eez, landlocked$iso3c)
## Aland = Lumped with Finland's Baltic sea
## HongKong, Macao = lumped with China, not possible to separate from EEZ map
## Ilse of Man grouped with Irish Sea area Between UK and Ireland
## NOTES:
# Overlapping claim South China Sea part of the South China Sea is counted with China in EEZ map

## Find matches to missing regions
grep("Mac", EEZ_shape$MARREGION, value=TRUE)

finding <- EEZ_shape %>%
filter(MARREGION  == "United Kingdom part of the Irish Sea and St. George's Channel")
plot(st_geometry(finding))

finding <- EEZ_shape %>%
filter(ISO_TER1  == "GBR")
plot(st_geometry(finding))
#mapview::mapview(finding)

## Check reverse: regions in EEZ map not in our master list
no_eez <- setdiff(EEZ_shape$ISO_TER1, master_rgns$iso3c)

check <- EEZ_shape %>%
  filter(ISO_TER1=="UMI")

## Question: I included the following in the administrative territory.  Does this seem reasonable?
## Method: replace ISO_Ter1 with ISO_SOV1
# ATF French Southern Territories: no inhabitants
# UMI United States Minor Outlying Islands, no inhabitants
# HMD Heard and McDonald Islands, no inhabitants, australian territory
# SGS South Georgia and the South Sandwich Islands, british overseas territory

# ATA Antarctica: keep this as is

EEZ_shape <- EEZ_shape %>%
  mutate(ISO_TER1 = ifelse(ISO_TER1 %in% c("ATF", "UMI", "HMD", "SGS"), ISO_SOV1, ISO_TER1))
setdiff(EEZ_shape$ISO_TER1, master_rgns$iso3c)  # should now only be ATA and NA

## Indicate HS areas (may want to make this more specific at some point)
EEZ_shape <- EEZ_shape %>%
  mutate(ISO_TER1 = ifelse(is.na(ISO_TER1) & is.na(ISO_SOV1), "HS", ISO_TER1))
setdiff(EEZ_shape$ISO_TER1, master_rgns$iso3c)  # should now only be ATA and NA

filter(EEZ_shape, is.na(ISO_TER1))

## assign remaining territories to administrative country
regions <- EEZ_shape %>%
  filter(is.na(ISO_TER1)) 
unique(regions$TERRITORY1)

EEZ_shape <- EEZ_shape %>%
  mutate(ISO_TER1 = ifelse(is.na(ISO_TER1), ISO_SOV1, ISO_TER1))
setdiff(EEZ_shape$ISO_TER1, master_rgns$iso3c)  # should now only be ATA and HS
sum(is.na(EEZ_shape$ISO_TER1))

# save shapefile
st_write(EEZ_shape, "/home/shares/food-systems/Food_footprint/dataprep/spatial/eez_rgns.shp")

```


## Now convert to raster!
The EEZs will have the same ID_0 values used in the regions list.

```{r}
EEZ_raster_start <- EEZ_shape %>%
  dplyr::select(iso3c = ISO_TER1) %>%
  left_join(master_rgns, by="iso3c")

check <- filter(EEZ_raster_start, is.na(ID_0))
table(check$iso3c)

EEZ_raster_start <- EEZ_raster_start %>%
  mutate(ID_0 = ifelse(iso3c=="ATA", 10, ID_0)) %>%
  mutate(ID_0 = ifelse(iso3c=="HS", 500, ID_0))

filter(EEZ_raster_start, is.na(ID_0))
summary(EEZ_raster_start)

EEZ_raster <- fasterize(EEZ_raster_start, food_raster, field="ID_0")
plot(EEZ_raster)

writeRaster(EEZ_raster, "/home/shares/food-systems/Food_footprint/dataprep/spatial/eez_rgns.tif", overwrite=TRUE)

EEZ_raster_start$area_km2 <- st_area(EEZ_raster_start)/1000000

eez_data <- st_drop_geometry(EEZ_raster_start) %>%
  dplyr::group_by(Country, iso3c, ID_0) %>%
  dplyr::summarize(area_km2 = sum(area_km2)) %>%
  unique() %>%
  arrange(iso3c) %>%
  mutate(Country = ifelse(iso3c=="ATA", "Antarctica", Country)) %>%
  mutate(Country = ifelse(iso3c == "HS", "High Seas", Country))

setdiff(eez_data$iso3c, master_rgns$iso3c)  # 2 extra regions in ocean data
no_eez <- setdiff(master_rgns$iso3c, eez_data$iso3c)  # 48 extra regions in land data
setdiff(no_eez, landlocked$iso3c) # 4 regions we were unable to get distinct EEZ's for.

write_csv(eez_data, here("_spatial/output/eez_rgns.csv"))

```


### Extend the EEZ rasters 4 cells inland to capture coastal cells

This is especially a problem for salmon aquaculture because it is located so close to shore in complex coastlines..
and these cells are often identified as ocean, especially given the scale of our raster cells.
```{r}

eez <- raster("/home/shares/food-systems/Food_footprint/dataprep/spatial/eez_rgns.tif")
eez_mol <- projectRaster(eez, crs="+proj=moll +lon_0=0 +x_0=0 +y_0=0 +ellps=WGS84 +datum=WGS84 +units=m +no_defs ", method="ngb", over=TRUE)
plot(eez_mol)
#click(eez_mol)

## Function to gapfill NA cells using most common value of surrounding cells
getmode <- function(v) {
   uniqv <- na.omit(unique(v))
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
gf_raster <- function(x){raster::focal(x, w = matrix(1,3,3), fun = getmode, pad = TRUE, NAonly=TRUE)}

r <- eez_mol

#2 cells out
i <- 0

while (i <= 2){

r <- gf_raster(r)

i <- i + 1
print(i)
}

plot(r)

rtest <-r  
rtest[r>0] <- 1000
plot(rtest, col="blue")
#zoom(rtest)
plot(eez_mol, col="red", add=TRUE)

r_latlong <- projectRaster(r, food_raster, method="ngb")
plot(r_latlong)
vals_r <- getValues(r_latlong)
table(vals_r)

writeRaster(r_latlong, "/home/shares/food-systems/Food_footprint/dataprep/spatial/eez_extended_rgns.tif", overwrite=TRUE)
```