---
title: "aligning_EEZ"
author: "Juliette"
date: "4/14/2020"
output: html_document
editor_options: 
  chunk_output_type: console
---

This markdown aligns EEZs to our region list.


```{r}
library(tidyverse)
library(dplyr)
library(raster)
library(rgdal)
library(sf)
library(fasterize)
library(readr)
library(here)
library(mapview)
library(countrycode)

prep <- "/home/shares/food-systems/Food_footprint/dataprep/"

## gall_peters projection
gall_peters <- "+proj=cea +lon_0=0 +x_0=0 +y_0=0 +lat_ts=45 +ellps=WGS84 +datum=WGS84 +units=m +no_defs"

#raster template 
template_eq_area <- raster("/home/shares/food-systems/Food_footprint/stressor_summary_new/feed_farm_system_stressor/farm_broiler_water_per_cell.tif")


master_rgns <- read_csv(here("_spatial/output/master_rgns.csv"))


```

## EEZ raster 
Created in eez_regions.Rmd
```{r}

EEZ_shape <- st_read("/home/shares/food-systems/Food_footprint/dataprep/spatial/eez_rgns.shp")
```

## Now convert to raster!
The EEZs will have the same ID_0 values used in the regions list.

```{r}
EEZ_raster_start <- EEZ_shape %>%
  dplyr::select(iso3c = ISO_TER1) %>%
  left_join(master_rgns, by="iso3c")

check <- filter(EEZ_raster_start, is.na(ID_0))
table(check$iso3c)

EEZ_raster_start <- EEZ_raster_start %>%
  mutate(ID_0 = ifelse(iso3c=="ATA", 10, ID_0)) %>%
  mutate(ID_0 = ifelse(iso3c=="HS", 500, ID_0))

filter(EEZ_raster_start, is.na(ID_0))
summary(EEZ_raster_start)

```


Convert to gall peters coordinate reference system.
```{r}

EEZ_raster_start_dateline <- EEZ_raster_start %>%
  st_wrap_dateline(c("WRAPDATELINE=YES"))

# for some reason, losing the "MULTIPOLYGON" designation...this action recovers it.
EEZ_raster_start_dataline_shape <- as(EEZ_raster_start_dateline, 'Spatial')
EEZ_raster_start_dateline <- st_as_sf(EEZ_raster_start_dataline_shape)

## Transform to equal area
EEZ_gp <- sf::st_transform(EEZ_raster_start_dateline, crs(template_eq_area)) 
plot(st_geometry(EEZ_gp))
plot(st_geometry(EEZ_raster_start))

## rasterize
EEZ_raster <- fasterize(EEZ_gp, template_eq_area, field="ID_0")
plot(EEZ_raster)

writeRaster(EEZ_raster, "/home/shares/food-systems/Food_footprint/dataprep/spatial/eez_rgns_gall_peters.tif", overwrite=TRUE)


```


### Extend the EEZ rasters 4 cells inland to capture coastal cells

This is especially a problem for salmon aquaculture because it is located so close to shore in complex coastlines..
and these cells are often identified as ocean, especially given the scale of our raster cells.
```{r}


## Function to gapfill NA cells using most common value of surrounding cells
getmode <- function(v) {
   uniqv <- na.omit(unique(v))
   uniqv[which.max(tabulate(match(v, uniqv)))]
}
gf_raster <- function(x){raster::focal(x, w = matrix(1,3,3), fun = getmode, pad = TRUE, NAonly=TRUE)}

r <- EEZ_raster

#2 cells out
i <- 0

while (i <= 2){

r <- gf_raster(r)

i <- i + 1
print(i)
}

plot(r)

rtest <-r  
rtest[r>0] <- 1000

plot(rtest, col="blue")
#crop_vals <- zoom(rtest)

rtest_crop <- crop(rtest, crop_vals)
plot(rtest_crop, col="blue")

rgn_raster_crop <- crop(EEZ_raster, crop_vals)
plot(rgn_raster_crop, col="red", add=TRUE)

#this looks good!
# crop because extending raster can create extra rows, etc.
r_crop <- crop(r, extent(template_eq_area))

writeRaster(r_crop, "/home/shares/food-systems/Food_footprint/dataprep/spatial/eez_extended_rgns_gall_peters.tif", overwrite=TRUE)

```