---
title: "Untitled"
author: "Caitie"
date: '2022-07-06'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(tidyverse)
library(here)
library(data.table)
library(raster)
library(tabularaster)

options(scipen = 999)
```

```{r}
un_geopolitical <- read_csv("/home/shares/food-systems/Food_footprint/chicken_salmon/_spatial/UNSD_Methodology.csv") %>%
  rename(georegion=Region_Name) %>% 
  dplyr::select(iso3c, georegion)

rgns <- raster("/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/spatial/land_eez_rgns.tif")
#plot(rgns)

rgn_names <- read_csv("/home/shares/food-systems/Food_footprint/chicken_salmon/_spatial/master_rgns.csv") %>%
  rename(land_area_km2 = area_km2)

eez_rgns <- read_csv("/home/shares/food-systems/Food_footprint/chicken_salmon/_spatial/eez_rgns.csv") %>%
  rename(eez_area_km2 = area_km2)

rescaling_values <- read_csv(here("_analysis/rescale_values.csv")) 
```
# Land and sea area

```{r}
land_area<-sum(rgn_names$land_area_km2,na.rm = T)
eez_area<-sum(eez_rgns$eez_area_km2, na.rm = T)
```

# Results from Step 6 zonal states
```{r}
results<-read.csv(here("_analysis/output_data/sum_pressures_country.csv"))
```

# Production

```{r}
broiler_prod<-read.csv("/home/shares/food-systems/Food_footprint/chicken_salmon/production/broiler_production.csv")
salmon_prod<-read.csv("/home/shares/food-systems/Food_footprint/chicken_salmon/production/salmon_production.csv")
```

# CPI rasters
```{r}
chicken<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/chickens_cumulative_stress.tif")

chicken2<-chicken/1000000

chicken_df<-rasterToPoints(chicken2) %>% 
  as.data.frame()
```

```{r}
salmon <- raster("/home/shares/food-systems/Food_footprint/chicken_salmon/rescaled_cumulative_pressure/salmon_cumulative_stress.tif")

salmon2<-salmon/1000000

salmon_df<-rasterToPoints(salmon2) %>% 
  as.data.frame()
```

# Mapping cumulative pressures of farmed chicken and salmon

## Maximum chicken CPI cell
```{r}
max(chicken_df$chickens_cumulative_stress)
```

```{r}
max(salmon_df$salmon_cumulative_stress)
```

## Percent of cells with CPI>0

```{r}
length(which(chicken_df$chickens_cumulative_stress>0))/nrow(chicken_df)
```

```{r}
length(which(salmon_df$salmon_cumulative_stress>0))/nrow(salmon_df)
```
## Percent of cells containing 95% of CPI

```{r}
cumsum_broiler<-chicken_df %>% 
  arrange(desc(chickens_cumulative_stress)) %>% 
  mutate(cumsum = cumsum(chickens_cumulative_stress),
         prop_cpi = cumsum/sum(chicken_df$chickens_cumulative_stress,na.rm = T))
         
broiler_95<-cumsum_broiler %>% 
  filter(prop_cpi<=0.95)

nrow(broiler_95)/nrow(chicken_df)
max(broiler_95$prop_cpi)
```

```{r}
cumsum_salmon<-salmon_df %>% 
  arrange(desc(salmon_cumulative_stress)) %>% 
  mutate(cumsum = cumsum(salmon_cumulative_stress),
         prop_cpi = cumsum/sum(salmon_df$salmon_cumulative_stress,na.rm = T))
         
salmon_95<-cumsum_salmon %>% 
  filter(prop_cpi<=0.95)

nrow(salmon_95)/nrow(salmon_df)
max(salmon_95$prop_cpi)
```

## Number of producing countries

```{r}
nrow(broiler_prod)
length(which(broiler_prod$broiler_slaughter_wt_tonnes>0))
length(which(broiler_prod$broiler_slaughter_wt_tonnes>0))/nrow(broiler_prod)
```

```{r}
nrow(salmon_prod)
length(which(salmon_prod$fao_tonnes_production>0))
length(which(salmon_prod$fao_tonnes_production>0))/244
```

## Country CPI

```{r}
iso3_broiler_cpi<-results %>%
    filter(!is.na(Country)) %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total) %>%
   group_by(iso3c, Country, animal_system) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE),
            variance_chi = var(prop_of_global, na.rm = T)) %>%
  filter(animal_system == "chickens")


# Salmon CPI
iso3_salmon_cpi<-results %>%
    filter(!is.na(Country)) %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total) %>%
   group_by(iso3c, Country, animal_system) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE),
            variance_chi = var(prop_of_global, na.rm = T)) %>%
  filter(animal_system == "salmon") 

write.csv(iso3_broiler_cpi, here("_analysis/figures/Country_results/Broiler_country_cpi.csv"))
write.csv(iso3_salmon_cpi, here("_analysis/figures/Country_results/Salmon_country_cpi.csv"))

```

Countries that make up 75% of CPI for chicken and salmon

``````{r}
iso3_broiler_cpi2<-iso3_broiler_cpi %>% 
  arrange(desc(country_farm_feed_chi)) %>% 
  ungroup() %>% 
  mutate(cpi_cumsum = cumsum(country_farm_feed_chi),
         prop_cpi = cpi_cumsum/sum(iso3_broiler_cpi$country_farm_feed_chi, na.rm = T)) 


broiler_75<-iso3_broiler_cpi2[which(iso3_broiler_cpi2$prop_cpi<=0.75),]

unique(broiler_75$Country)
```

```{r}
iso3_salmon_cpi2<-iso3_salmon_cpi %>% 
  arrange(desc(country_farm_feed_chi)) %>% 
  ungroup() %>% 
  mutate(cpi_cumsum = cumsum(country_farm_feed_chi),
         prop_cpi = cpi_cumsum/sum(iso3_salmon_cpi$country_farm_feed_chi, na.rm = T)) 


salmon_75<-iso3_salmon_cpi2[which(iso3_salmon_cpi2$prop_cpi<=0.75),]

unique(salmon_75$Country)
```

```{r}
all_75<-rbind(broiler_75, salmon_75)

length(unique(all_75$Country))

which(broiler_75$Country %in% salmon_75$Country)
```

## Variance within countries

```{r}
cor.test(iso3_broiler_cpi$country_farm_feed_chi, iso3_broiler_cpi$variance_chi, type = "pearson")
cor.test(iso3_salmon_cpi$country_farm_feed_chi, iso3_salmon_cpi$variance_chi, type = "pearson")
```

## Land vs Sea CPI total and by country

```{r}
chicken_location<-results %>%  
  filter(!is.na(Country),
         animal_system == "chickens") %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total) %>%
   group_by(location) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE))
  

chicken_location$country_farm_feed_chi[1]/sum(chicken_location$country_farm_feed_chi)
```

```{r}
iso3_chicken_location<-results %>%  
  filter(!is.na(Country),
         animal_system == "chickens") %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total) %>%
   group_by(iso3c, Country, location) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE))
  
```
```{r}
salmon_location<-results %>%  
  filter(!is.na(Country),
         animal_system == "salmon") %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total) %>%
   group_by(location) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE))
  

salmon_location$country_farm_feed_chi[1]/sum(salmon_location$country_farm_feed_chi)
```

```{r}
iso3_salmon_location<-results %>%  
  filter(!is.na(Country),
         animal_system == "salmon") %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total) %>%
   group_by(iso3c, Country, location) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE))
```

# Feed drives overlap for cumulative pressures

## CPI Overlap

```{r}
cell_count<-read.csv(here("_analysis/figures/overlap_map/data/cell_count.csv")) 

overlap <- cell_count %>% 
  filter(!category %in% c("zero chicken\nzero salmon", "high chicken\nzero salmon","low chicken\nzero salmon","zero chicken\nlow salmon","zero chicken\nmedium salmon","zero chicken\nhigh salmon","medium chicken\nzero salmon"))

no_zero_zero<-cell_count %>% 
  filter(!category %in% c("zero chicken\nzero salmon"))

sum(overlap$number_cells)/sum(no_zero_zero$number_cells) #85.5% overlap

```

# Feed CPI

```{r}
broiler_cpi_feed<-results %>%
    filter(!is.na(Country)) %>% ## Antarctica
  left_join(rescaling_values, by= c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total,
         source2 = ifelse(source == "farm", "farm", "feed")) %>%
   group_by(animal_system, source2) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE)) %>%
  filter(animal_system == "chickens") 

broiler_cpi_feed<-broiler_cpi_feed %>% 
  mutate(prop = country_farm_feed_chi/sum(broiler_cpi_feed$country_farm_feed_chi))


# Salmon CPI
salmon_cpi_feed<-results %>%
    filter(!is.na(Country)) %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total,
         source2 = ifelse(source == "farm", "farm", "feed")) %>%
   group_by(animal_system, source2) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE)) %>%
  filter(animal_system == "salmon") 

salmon_cpi_feed<-salmon_cpi_feed %>% 
  mutate(prop = country_farm_feed_chi/sum(salmon_cpi_feed$country_farm_feed_chi))
```

```{r}
broiler_cpi_feed$prop[broiler_cpi_feed$source2 == "feed"]
salmon_cpi_feed$prop[salmon_cpi_feed$source2 == "feed"]
```

# Feed stats

```{r}
animal_stressor_feed<-results %>% 
  mutate(source2 = ifelse(source == "farm", "farm", "feed")) %>% 
  group_by(animal_system, stressor, source2) %>% 
  summarise(total_pressure = sum(value, na.rm = T)) 

animal_stressor_feed_location<-results %>% 
   mutate(source2 = ifelse(source == "farm", "farm", "feed")) %>% 
  group_by(animal_system, stressor, source2, location) %>% 
  summarise(total_pressure = sum(value, na.rm = T)) 

animal_stressor_feed2<-animal_stressor_feed %>% 
  group_by(animal_system, stressor) %>% 
  summarise(sum_pressures = sum(total_pressure)) %>% 
  full_join(animal_stressor_feed) %>% 
  mutate(prop= total_pressure/sum_pressures)
```

```{r}
# Chicken CPI
broiler_cpi_feed_farm_iso3<-results %>%
    filter(!is.na(Country)) %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total,
         source2 = ifelse(source == "farm", "farm", "feed")) %>%
   group_by(iso3c, Country, animal_system, source2) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE)) %>%
  filter(animal_system == "chickens") 

# Salmon CPI

salmon_cpi_feed_farm_iso3<-results %>%
    filter(!is.na(Country)) %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total,
         source2 = ifelse(source == "farm", "farm", "feed")) %>%
   group_by(iso3c, Country,animal_system, source2) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE)) %>%
  filter(animal_system == "salmon") 

write.csv(broiler_cpi_feed_farm_iso3, here("_analysis/output_data/Broiler_farm_feed_cpi.csv"))

write.csv(salmon_cpi_feed_farm_iso3, here("_analysis/output_data/Salmon_farm_feed_cpi.csv"))
```

```{r}
feed_location<-results %>%
    filter(!is.na(Country)) %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total,
         source2 = ifelse(source == "farm", "farm", "feed")) %>%
   group_by(source2, stressor, location) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE)) %>%
  filter(#animal_system == "salmon",
         source2 == "feed") %>% 
  mutate(cpi_km2 = ifelse(location == "land", country_farm_feed_chi/(land_area),
                               country_farm_feed_chi/(eez_area)))

feed_location

test<-results %>% 
 filter(stressor == "disturbance") %>% 
  mutate(source2 = ifelse(source == "farm", "farm", "feed")) %>% 
  group_by(source2, location) %>% 
  summarise(total_dist = sum(value)) %>% 
  filter(source2 == "feed")

test
```


# Comparing environmental efficiency of production

```{r}
chicken_disturb<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/chickens_disturbance_per_cell.tif")

salmon_disturb<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/salmon_disturbance_per_cell.tif")

all_chick_dist<-cellStats(chicken_disturb, "sum", na.rm = T)
all_salmon_dist<-cellStats(salmon_disturb, "sum", na.rm = T)

```

```{r}
chicken_nutri<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/chickens_nutrient_per_cell.tif")

salmon_nutri<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/salmon_nutrient_per_cell.tif")

all_chick_nutri<-cellStats(chicken_nutri, "sum", na.rm = T)
all_salmon_nutri<-cellStats(salmon_nutri, "sum", na.rm = T)

```

```{r}
chicken_fw<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/chickens_water_per_cell.tif")

salmon_fw<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/salmon_water_per_cell.tif")

all_chick_fw<-cellStats(chicken_fw, "sum", na.rm = T)
all_salmon_fw<-cellStats(salmon_fw, "sum", na.rm = T)

```

```{r}
chicken_ghg<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/chickens_ghg_per_cell.tif")

salmon_ghg<-raster("/home/shares/food-systems/Food_footprint/chicken_salmon/raw_pressure_summary/system_stressor/salmon_ghg_per_cell.tif")

all_chick_ghg<-cellStats(chicken_ghg, "sum", na.rm = T)
all_salmon_ghg<-cellStats(salmon_ghg, "sum", na.rm = T)

```

How many times greater is chicken than salmon across pressures?

```{r}
sum(broiler_prod$broiler_slaughter_wt_tonnes, na.rm = T)/sum(salmon_prod$fao_tonnes_production,na.rm = T)
sum(broiler_prod$broiler_slaughter_wt_tonnes, na.rm = T)/1000000
sum(salmon_prod$fao_tonnes_production,na.rm = T)/1000000
```

```{r}
all_chick_dist/all_salmon_dist
all_chick_dist
all_salmon_dist
```

```{r}
all_chick_nutri/all_salmon_nutri
all_chick_ghg/all_salmon_ghg
all_chick_fw/all_salmon_fw

```

## Efficiency - CPI/production

On-farm

```{r}
broiler_cpi_prod<-full_join(iso3_broiler_cpi, broiler_prod, by = c("iso3c", "Country"))

salmon_cpi_prod<-full_join(iso3_salmon_cpi, salmon_prod, by = c("iso3c")) %>% 
  mutate(fao_tonnes_production = ifelse(is.na(fao_tonnes_production) == T, 0 , as.numeric(fao_tonnes_production)))
```


```{r}
iso3_broiler_cpi_farm_prod<-broiler_cpi_feed_farm_iso3 %>% 
  filter(source2 == "farm") %>% 
  full_join(broiler_prod) %>% 
  mutate(cpi_prod = country_farm_feed_chi/broiler_slaughter_wt_tonnes) %>% 
  dplyr::select(iso3c, Country, country_farm_feed_chi, broiler_slaughter_wt_tonnes, cpi_prod) 

sub_farm_prod<- iso3_broiler_cpi_farm_prod %>% 
  filter(iso3c %in% c("USA", "BRA", "CHN"))

iso3_salmon_cpi_farm_prod<-salmon_cpi_feed_farm_iso3 %>% 
  filter(source2 == "farm") %>% 
  full_join(salmon_prod) %>% 
  mutate(cpi_prod = country_farm_feed_chi/fao_tonnes_production) %>% 
  dplyr::select(iso3c, Country, country_farm_feed_chi, fao_tonnes_production, cpi_prod)

write.csv(iso3_broiler_cpi_farm_prod,here("_analysis/output_data/Broiler_farm_cpi_prod.csv"))

write.csv(iso3_salmon_cpi_farm_prod,here("_analysis/output_data/Salmon_farm_cpi_prod.csv"))
```


```{r}
iso3_broiler_cpi_farm_pressure<-results %>%
    filter(!is.na(Country),
           animal_system == "chickens",
           source == "farm") %>% ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total) %>%
   group_by(iso3c, Country, animal_system, stressor) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE),
            variance_chi = var(prop_of_global, na.rm = T)) %>% 
  filter(iso3c %in% c("USA", "BRA", "CHN"))


# Salmon CPI
iso3_salmon_cpi_farm_pressure<-results %>%
    filter(!is.na(Country),
           source == "farm") %>%  ## Antarctica
  left_join(rescaling_values, by=c("stressor" = "pressure")) %>%
  rowwise() %>%
  mutate(prop_of_global = value/global_total) %>%
   group_by(iso3c, Country, animal_system, stressor) %>%
  summarize(country_farm_feed_chi = sum(prop_of_global, na.rm=TRUE),
            variance_chi = var(prop_of_global, na.rm = T)) %>%
  filter(animal_system == "salmon") %>% 
  filter(iso3c %in% c("NOR", "CHL", "CAN", "GBR"))
```

Feed
```{r}
crop_feed_cpi<-read.csv(here("chicken_salmon_diet/feed_cpi_per_tonne_crop.csv")) %>% 
  rename(crop_tonnes = tonnes_feed,
         crop_cpi = cpi)


fofm_feed_cpi<-read.csv(here("chicken_salmon_diet/feed_cpi_per_tonne_fofm.csv")) %>% 
  rename(fofm_tonnes = tonnes_feed,
         fofm_cpi = cpi)

chicken_crop_feed_cpi<-crop_feed_cpi %>% 
  filter(system == "feed_land_chickens_industrial_meat",
         crop_tonnes>0)

salmon_crop_feed_cpi<-crop_feed_cpi %>% 
  filter(system == "feed_marine_salmon_aquaculture_meat",
         crop_tonnes>0) 

chicken_fofm_feed_cpi<-fofm_feed_cpi %>% 
  filter(system == "feed_land_chickens_industrial_meat",
         fofm_tonnes>0)

salmon_fofm_feed_cpi<-fofm_feed_cpi %>% 
  filter(system == "feed_marine_salmon_aquaculture_meat",
         fofm_tonnes>0) 
```

```{r}
crop_fofsm<-full_join(crop_feed_cpi, fofm_feed_cpi, by = c("iso3c", "country", "system")) %>% 
  dplyr::select(-cpi_per_tonne.x, -cpi_per_tonne.y) %>% 
  mutate(feed_tonnes = crop_tonnes + fofm_tonnes,
         feed_cpi = crop_cpi + fofm_cpi,
         cpi_per_tonne = feed_cpi/feed_tonnes)

chicken_crop_fofsm<-crop_fofsm %>% 
  filter(system == "feed_land_chickens_industrial_meat",
         feed_tonnes>0) #%>% 
  #dplyr::select(iso3c, country, feed_tonnes, feed_cpi, cpi_per_tonne)


salmon_crop_fofsm<-crop_fofsm %>% 
  filter(system == "feed_marine_salmon_aquaculture_meat",
         feed_tonnes>0) #%>% 
  #dplyr::select(iso3c, country, feed_tonnes, feed_cpi, cpi_per_tonne)

write.csv(chicken_crop_fofsm,here("_analysis/output_data/Broiler_feed_cpi_prod.csv"))

write.csv(salmon_crop_fofsm,here("_analysis/output_data/Salmon_feed_cpi_prod.csv"))
```

# Efficiency CPI/area

```{r}
cpi_pixel<-read.csv(here("_analysis/output_data/CPI_cells_by_country_top95perc.csv"))

```

